%! AP Statistics — Unit 3, Lesson 3.2 — Homework
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

\begin{document}

\pageheader{Unit 3, Lesson 3.2}{Homework}
\namedateperiod

\vspace{0.1in}

\begin{practicebox}
\small
For each study, classify it as an observational study or an experiment, identify
whether random selection and/or random assignment were used, and state what
conclusions are valid.

\vspace{8pt}
\textbf{1.} A nutritionist randomly selects 500 adults from the city directory and
asks each one about fruit and vegetable consumption and blood pressure. High consumers
have significantly lower blood pressure.

\vspace{6pt}
Study type: \blank{5cm} \quad Random selection? \blank{2cm} \quad Random assignment? \blank{2cm}\\[6pt]
Can we conclude diet \emph{causes} lower BP? \blank{3cm} \quad Generalize to city adults? \blank{3cm}\\[6pt]
Explain: \writeline\\[1pt]\writeline

\vspace{8pt}
\textbf{2.} A tech company recruits 80 employees and randomly assigns 40 to a
standing-desk program and 40 to regular desks. After 3 months, the standing-desk
group reports significantly less back pain.

\vspace{6pt}
Study type: \blank{5cm} \quad Random selection? \blank{2cm} \quad Random assignment? \blank{2cm}\\[6pt]
Can we conclude standing desks \emph{caused} less pain? \blank{3cm}\\[6pt]
Can we generalize to all office workers? \blank{3cm}\\[6pt]
Explain: \writeline\\[1pt]\writeline

\vspace{8pt}
\textbf{3.} Free Response Practice:\\
\textit{A researcher wants to determine whether a new reading intervention improves
comprehension. She has 60 third-grade students from a single school who volunteer
to participate. She randomly assigns 30 to the intervention and 30 to a control
group. After 6 weeks, students in the intervention group score significantly higher.}

\vspace{6pt}
\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=8pt]
  \item Can we conclude the intervention caused higher scores? Explain.\\
        \writeline\\[1pt]\writeline
  \item Can we generalize to all third-graders? Explain.\\
        \writeline\\[1pt]\writeline
  \item What change to the study design would allow generalization?\\
        \writeline\\[1pt]\writeline
\end{enumerate}
\end{practicebox}

\end{document}
