%! AP Statistics — Unit 4, Lesson 4.3 — Homework KEY
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-key}

\begin{document}

\pageheader{Unit 4, Lesson 4.3}{Homework --- KEY}
\namedateperiod

\vspace{0.1in}

\begin{practicebox}
\small

\textbf{1.} Marbles: 5 red, 4 blue, 1 yellow.
\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=5pt]
  \item \ans{10 outcomes.}
  \item \ans{$P(\text{red}) = 5/10 = 0.5$; \quad $P(\text{blue}) = 4/10 = 0.4$; \quad $P(\text{yellow}) = 1/10 = 0.1$}
  \item \ans{$0.5 + 0.4 + 0.1 = 1.0$ \checkmark}
  \item \ans{$P(\text{not blue}) = 1 - 0.4 = 0.6$}
  \item \ans{If a marble is drawn and replaced many times, about half of all draws will be red in the long run.}
\end{enumerate}

\vspace{6pt}
\textbf{2.} Blood types.
\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=5pt]
  \item \ans{$0.44 + 0.42 + 0.10 + 0.04 = 1.00$ \checkmark}
  \item \ans{$P(\text{not O}) = 1 - 0.44 = 0.56$; \quad $P(\text{A or B}) = 0.42 + 0.10 = 0.52$}
  \item \ans{If patients are randomly selected from this clinic's records over many selections, about 44\% will have type O blood in the long run.}
\end{enumerate}

\vspace{6pt}
\textbf{3.} Two dice.
\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=5pt]
  \item \ans{Matching pairs: (1,1),(2,2),(3,3),(4,4),(5,5),(6,6) → 6 outcomes. $P = 6/36 = 1/6$.}
  \item \ans{Sum = 2: only (1,1); sum = 12: only (6,6). Total: 2 outcomes. $P = 2/36 = 1/18$.}
  \item \ans{$P(\text{not 2 or 12}) = 1 - 1/18 = 17/18$.}
  \item \ans{$P(\text{sum}=7) = 6/36 = 1/6$; $P(\text{sum}\ne7) = 30/36 = 5/6$. Sum: $1/6 + 5/6 = 1$ \checkmark}
\end{enumerate}

\vspace{6pt}
\textbf{4.} AP-Style: Green/yellow/purple marbles.
\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=5pt]
  \item \ans{$P(\text{green}) = 4/8 = 1/2 = 0.5$; $P(\text{not green}) = 1 - 0.5 = 0.5$.}
  \item \ans{The student is wrong. $P(\text{purple}) = 1/8 = 0.125$, not 0. A probability of 0 means the event is impossible --- but purple marbles exist in the bag, so drawing one is possible (just uncommon). Rare $\ne$ impossible.}
  \item \ans{If one marble is drawn and replaced many times, about 3 out of every 8 draws will be yellow in the long run.}
\end{enumerate}

\vspace{6pt}
\textbf{5.} AP-Style: \ans{(C)} \textcolor{keyred}{\textbf{$\leftarrow$ correct}}
\begin{enumerate}[label=(\Alph*), leftmargin=2em, itemsep=2pt]
  \item Incorrect --- $2/5$ is $P(\text{red})$, not $P(\text{not red})$.
  \item Incorrect --- this would be $P(\text{not red})$ if there were only 3 sections.
  \item \textbf{Correct} --- $P(\text{not red}) = 1 - 2/5 = 3/5$.
  \item Incorrect --- $1/5$ is $P(\text{green})$.
\end{enumerate}

\vspace{6pt}
\textbf{Extension / Preview:}
\ans{$P(\text{red}) = 2/6 = 1/3$, so 2 red sections. $P(\text{blue}) = 3/6 = 1/2$, so 3 blue sections. Remaining: $6 - 2 - 3 = 1$ section. $P(\text{remaining}) = 1/6$. The remaining color (call it green) fills 1 of the 6 sections.}

\end{practicebox}

\end{document}
