%! AP Statistics — Unit 1, Lesson 1.10 — Homework
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

%=============================================================================
\begin{document}

\pageheader{Unit 1, Lesson 1.10}{Homework: The Normal Distribution}
\namedateperiod

\vspace{0.10in}

\begin{tcolorbox}[colback=sky, colframe=navy, boxrule=0.8pt, arc=2mm,
    left=3mm, right=3mm, top=1.5mm, bottom=1.5mm]
\small Show all $z$-score calculations. Interpret every probability in context.
Use Table A or technology; indicate which you used.
\end{tcolorbox}

\vspace{0.12in}

% ════════════════════════════════════════════════════════════════════════════
% PART A — Empirical Rule
% ════════════════════════════════════════════════════════════════════════════
\begin{blurbbox}[Part A \quad The Empirical Rule]{navylight}
\small

IQ scores on a widely used test are approximately Normally distributed with
mean $\mu = 100$ and standard deviation $\sigma = 15$. Use the
68--95--99.7 Rule for all questions in this part (do not use Table A).

\vspace{0.10in}

\begin{enumerate}[leftmargin=1.5em, itemsep=8pt]

  \item Fill in the IQ values at each labeled point on the axis below.\\[6pt]
        \begin{center}
        \begin{tikzpicture}[scale=1.0]
          \draw[thick, navy]
            plot[domain=-3.5:3.5, samples=80] (\x, {2.2*exp(-\x*\x/2)});
          \draw[thick] (-3.8, 0) -- (3.8, 0);
          \foreach \z in {-3,-2,-1,0,1,2,3} {
            \draw (\z, -0.12) -- (\z, 0.12);
            \node[below, font=\small] at (\z, -0.15) {\blank{1.5cm}};
          }
          \node[below, font=\small\itshape] at (0, -0.55) {IQ score};
          \node[above, font=\small\bfseries\color{navy}] at (0, 2.22) {$\mu = 100$};
        \end{tikzpicture}
        \end{center}

  \item What percentage of people have IQ scores between 85 and 115?
        Between 70 and 130? Show reasoning.\\[5pt]
        Between 85 and 115: \blank{2cm}\% \quad Between 70 and 130: \blank{2cm}\%

  \item What percentage of people have IQ scores \textbf{above} 130?\\[5pt]
        \writeline

  \item A person's IQ is reported as 145. Using the Empirical Rule, comment on how
        unusual this score is.\\[5pt]
        \writeline\\[1pt]\writeline

\end{enumerate}

\end{blurbbox}

\vspace{0.12in}

% ════════════════════════════════════════════════════════════════════════════
% PART B — z-scores and Normal table
% ════════════════════════════════════════════════════════════════════════════
\begin{blurbbox}[Part B \quad $z$-Scores and the Normal Table]{greenacc}
\small

Customer wait times at a coffee shop are approximately $N(4.5,\,1.2)$ minutes
(mean 4.5 min, SD 1.2 min).

\vspace{0.10in}

\begin{enumerate}[leftmargin=1.5em, itemsep=8pt]

  \item A customer waited 6 minutes. Calculate the $z$-score and interpret it.\\[5pt]
        $z = \blank{4cm} = \blank{2cm}$\quad
        Interpretation: \writeline

  \item Use Table A to find the proportion of customers who wait \textbf{more than}
        6 minutes. Show all steps.\\[5pt]
        $P(\text{wait} > 6) = 1 - P(Z < \blank{2cm}) = 1 - \blank{2cm} = \blank{2cm}$

  \item Find the proportion of customers who wait \textbf{between 3 and 6 minutes}.\\[5pt]
        $z(3) = \blank{3cm} = \blank{2cm}$\quad
        $z(6) = \blank{3cm} = \blank{2cm}$\\[4pt]
        $P(3 < \text{wait} < 6) = P(Z < \blank{2cm}) - P(Z < \blank{2cm}) = \blank{2cm} - \blank{2cm} = \blank{2cm}$

  \item Find the wait time at the \textbf{10th percentile}.
        ($z^* \approx -1.28$ for the 10th percentile.)\\[5pt]
        $x = \mu + z^* \cdot \sigma = \blank{6cm} = \blank{3cm}$ minutes

\end{enumerate}

\end{blurbbox}

\vspace{0.12in}

% ════════════════════════════════════════════════════════════════════════════
% PART C — AP-Style Free Response
% ════════════════════════════════════════════════════════════════════════════
\begin{blurbbox}[Part C \quad AP-Style Free Response]{redacc}
\small

Scores on a standardized graduate school entrance exam are approximately Normally
distributed with mean $\mu = 500$ and standard deviation $\sigma = 100$.

\vspace{0.08in}

\begin{enumerate}[leftmargin=1.5em, itemsep=8pt]

  \item What proportion of test-takers scored \textbf{above 650}?
        Show your $z$-score calculation, use Table A, and interpret the result.\\[5pt]
        \writeline\\[1pt]\writeline\\[1pt]\writeline

  \item What proportion scored \textbf{below 400}?\\[5pt]
        \writeline\\[1pt]\writeline

  \item What score separates the \textbf{top 5\%} of test-takers from the rest?
        ($z^* \approx 1.645$ for the 95th percentile.) Show your work.\\[5pt]
        \writeline\\[1pt]\writeline

  \item A graduate program requires a score of at least 650 for admission.
        Based on your answer to (a), comment on how selective this requirement is.\\[5pt]
        \writeline\\[1pt]\writeline

\end{enumerate}

\end{blurbbox}

\end{document}
