%! AP Statistics — Unit 9, Lesson 9.4 — Homework (Answer Key)
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-key}

\begin{document}

\pageheader{Unit 9, Lesson 9.4}{Homework --- Answer Key}
\namedateperiod

\vspace{0.1in}

\textbf{Problem 1.} A random sample of 28 college students was surveyed. The
explanatory variable is hours per week spent on social media ($x$) and the response
variable is GPA ($y$). A residual plot shows random scatter with no curve and constant
spread. The residuals appear approximately normal.

\begin{enumerate}[label=\alph*.]

  \item Name the appropriate inference procedure.

        \ans{$t$-test for slope}

  \item Define $\beta$ in context and state H$_0$ and H$_a$.

        $\beta = $ \ans{the true slope of the population regression line relating GPA
        to hours per week on social media for college students}

        H$_0$: \ans{$\beta = 0$} \quad H$_a$: \ans{$\beta \ne 0$}

  \item Verify each LINER condition:

        \ans{L: Met --- residual plot shows random scatter with no curve.
        I: Met --- random sample stated; need to assume the college population is at
        least $10 \times 28 = 280$ students (10\% condition).
        N: Met --- residuals approximately normal.
        E: Met --- residual plot shows constant spread.
        R: Met --- random sample stated.}

  \item \ans{The 10\% condition for I cannot be fully verified without knowing the
        total size of the college student population. If the college has fewer than
        280 students, the condition would not be met.}

\end{enumerate}

\vspace{0.1in}

\textbf{Problem 2.}

\begin{enumerate}[label=\alph*.]

  \item H$_0$: \ans{$\beta = 0$ (rainfall has no linear effect on umbrella sales)}

        H$_a$: \ans{$\beta \ne 0$ (rainfall is linearly related to umbrella sales)}

        $\beta = 0$ means: \ans{daily rainfall has no linear effect on umbrella
        sales in the population.}

  \item H$_0$: \ans{$\beta = 0$}

        H$_a$: \ans{$\beta > 0$ (one-sided: older runners take longer)}
        (also accept $\beta \ne 0$ as a two-sided alternative)

        $\beta = 0$ means: \ans{age has no linear effect on marathon finish time
        in the population.}

  \item H$_0$: \ans{$\beta = 0$}

        H$_a$: \ans{$\beta < 0$ (one-sided: larger classes score lower)}

        $\beta = 0$ means: \ans{class size has no linear effect on average exam
        score in the population.}

\end{enumerate}

\begin{teachernote}
For Problem 2b, the question says the researcher ``considers'' a one-sided test.
Accept either $\beta > 0$ (one-sided) or $\beta \ne 0$ (two-sided). The one-sided
alternative is appropriate only if the researcher committed to it before seeing the
data. For Problem 2c, note that the teacher's claim involves $\beta < -1$, but AP
convention tests H$_0$: $\beta = 0$; accept H$_a$: $\beta < 0$ as a valid simplification.
\end{teachernote}

\end{document}
