%! AP Statistics — Unit 1, Lesson 1.6 — Group Activity
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

%=============================================================================
\begin{document}

\pageheader{Unit 1, Lesson 1.6}{Group Activity: Writing \& Critiquing SOCS Descriptions}
\namepartnerperiod

\vspace{0.1in}

\begin{tcolorbox}[colback=sky, colframe=navy, boxrule=0.8pt, arc=2mm,
    left=3mm, right=3mm, top=2mm, bottom=2mm]
\small
\textbf{Part 1} (group, 8 min): Read the distribution summary and write a
complete SOCS description.\\[4pt]
\textbf{Part 2} (group, 5 min): Critique a sample student response.\\[4pt]
\textbf{Part 3} (individual, 3 min): Reflection.
\end{tcolorbox}

\vspace{0.14in}

% ── PART 1 ───────────────────────────────────────────────────────────────────
{\large\bfseries\color{navy} Part 1 \quad Write a Complete SOCS Description}

\vspace{0.1in}

\noindent\small Your group has been assigned one of the distributions below.
Read the description carefully, then write a complete SOCS description on the
lines provided. Every sentence must include context.

\vspace{0.1in}

\begin{tcolorbox}[colback=white, colframe=navy, boxrule=0.8pt, arc=2mm,
    left=3mm, right=3mm, top=2mm, bottom=2mm]
\small
\textbf{Distribution A --- Ages at a Concert ($n = 80$)}\\
A histogram of ages (in years) of 80 concert-goers shows two clear peaks:
one near 17--19 years and one near 35--40 years. There are no obvious outliers.
Ages range from 14 to 55 years. The overall center is near 27 years.

\vspace{6pt}
\textbf{Distribution B --- Wait Times at a Coffee Shop ($n = 50$)}\\
A dotplot of wait times (in minutes) for 50 customers shows most customers
wait 2--6 minutes. The distribution has a long tail to the right, with three
customers waiting more than 15 minutes (one waited 22 minutes). The center
is near 5 minutes; values range from 1 to 22 minutes.

\vspace{6pt}
\textbf{Distribution C --- Final Exam Scores ($n = 35$)}\\
A stemplot of final exam scores (out of 100) for 35 students shows scores
clustered between 70 and 95 points, with a long tail toward lower values.
Two students scored below 40 points, well below the rest of the class.
The center is near 82 points; scores range from 36 to 100.
\end{tcolorbox}

\vspace{0.12in}

\noindent\textbf{My group's distribution: \blank{3cm}} \hfill
\small (Circle: A \quad B \quad C)

\vspace{0.1in}

\noindent\textbf{Write your complete SOCS description below.}
Label each sentence with S, O, C, or S in the margin.

\vspace{6pt}
\writeline\\[1pt]\writeline\\[1pt]\writeline\\[1pt]\writeline\\[1pt]
\writeline\\[1pt]\writeline

\vspace{0.12in}

\begin{enumerate}[leftmargin=1.5em, itemsep=8pt]
  \item After sharing with the class, which SOCS component did most groups
        forget or write incompletely?\\[5pt]
        \writeline\\[1pt]\writeline

  \item How did including context change how your description sounded?
        What would be lost if you removed the variable name?\\[5pt]
        \writeline\\[1pt]\writeline
\end{enumerate}

\vspace{0.12in}

% ── PART 2 ───────────────────────────────────────────────────────────────────
{\large\bfseries\color{navy} Part 2 \quad Critique a Sample Response}

\vspace{0.1in}

\noindent\small A student wrote the following response to describe Distribution B
(wait times). Read it carefully and answer the questions.

\vspace{0.1in}

\begin{tcolorbox}[colback=redbg, colframe=redacc, boxrule=0.8pt, arc=2mm,
    left=3mm, right=3mm, top=2mm, bottom=2mm]
\small\textit{``The distribution is skewed right. The center is about 5.
The wait times go from 1 to 22. There are some outliers.''}
\end{tcolorbox}

\vspace{0.12in}

\begin{enumerate}[leftmargin=1.5em, itemsep=8pt]

  \item List every problem with the student's response. Be specific about
        which AP requirement is violated by each problem.\\[5pt]
        \writeline\\[1pt]\writeline\\[1pt]\writeline\\[1pt]\writeline

  \item Rewrite the student's response so it would earn full AP credit.
        Use complete sentences with context in every sentence.\\[5pt]
        \writeline\\[1pt]\writeline\\[1pt]\writeline\\[1pt]\writeline

\end{enumerate}

\vspace{0.12in}

% ── PART 3 ───────────────────────────────────────────────────────────────────
{\large\bfseries\color{navy} Part 3 \quad Individual Reflection}

\vspace{0.1in}

\begin{tcolorbox}[colback=goldbg, colframe=goldacc, boxrule=0.8pt, arc=2mm,
    left=3mm, right=3mm, top=2mm, bottom=2mm]
\small\textbf{In your own words:} Before today, how would you have described a
histogram to someone who hadn't seen it? How is a SOCS description different
from --- and better than --- that informal description?\\[6pt]
\writeline\\[1pt]\writeline\\[1pt]\writeline
\end{tcolorbox}

\end{document}
