%! AP Statistics — Unit 4, Lesson 4.5 — Homework
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

\begin{document}

\pageheader{Unit 4, Lesson 4.5}{Homework}
\namedateperiod

\vspace{0.1in}

\begin{practicebox}
\small
A school surveyed 240 students about their preferred study environment and their
GPA range. The results are shown below.

\vspace{6pt}
\renewcommand{\arraystretch}{1.4}
\begin{tabularx}{\linewidth}{@{} l X X X r @{}}
 & \textbf{Quiet Room} & \textbf{Music On} & \textbf{Group Study} & \textbf{Total} \\
\hline
\textbf{GPA 3.5--4.0} & 40 & 20 & 20 & 80 \\
\textbf{GPA 3.0--3.4} & 30 & 30 & 30 & 90 \\
\textbf{GPA below 3.0} & 20 & 30 & 20 & 70 \\
\hline
\textbf{Total}         & 90 & 80 & 70 & 240 \\
\end{tabularx}

\vspace{8pt}
One student is selected at random.

\vspace{8pt}
\textbf{1.} Write the formula for conditional probability, then use it to compute
$P(\text{GPA 3.5--4.0} | \text{Quiet Room})$. Show all steps.
\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=6pt]
  \item Formula: \blank{9cm}
  \item $P(\text{GPA 3.5--4.0} \cap \text{Quiet Room}) = $ \blank{4cm}
  \item $P(\text{Quiet Room}) = $ \blank{4cm}
  \item $P(\text{GPA 3.5--4.0} | \text{Quiet Room}) = $ \blank{5cm}
  \item Interpret in context: \writeline\writeline
\end{enumerate}

\vspace{8pt}
\textbf{2.} Compute $P(\text{Music On} | \text{GPA below 3.0})$. Show setup.\\
\blank{4cm} $\div$ \blank{4cm} $=$ \blank{3cm}

\vspace{8pt}
\textbf{3.} Use the multiplication rule to verify $P(\text{Group Study} \cap \text{GPA 3.0--3.4})$.
\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=6pt]
  \item $P(\text{Group Study}) = $ \blank{4cm}
  \item $P(\text{GPA 3.0--3.4} | \text{Group Study}) = $ \blank{4cm}
  \item Product = \blank{5cm} \quad Table cell / 240 = \blank{5cm} \quad Match? \blank{2cm}
\end{enumerate}

\vspace{8pt}
\textbf{4.} A student says: ``$P(\text{Quiet Room}|\text{GPA 3.5--4.0})$ is the same
as $P(\text{GPA 3.5--4.0}|\text{Quiet Room})$ because they both involve the same two events.''
\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=6pt]
  \item Compute both values. \writeline\writeline
  \item Is the student's claim correct? Explain the error. \writeline\writeline
\end{enumerate}

\vspace{8pt}
\textbf{5.} (AP Free-Response Style) In a complete sentence, interpret
$P(\text{GPA 3.5--4.0} | \text{Music On})$ in context.
First compute the value, then write your sentence.\\
Calculation: \blank{6cm}\\
Sentence: \writeline\writeline

\vspace{8pt}
\textbf{6.} (Extension) Is $P(\text{Quiet Room}|\text{GPA 3.5--4.0})$ greater than,
less than, or equal to $P(\text{Quiet Room})$? What might this suggest about
the relationship between studying in a quiet room and having a high GPA?
(Preview of independence, coming in Lesson 4.6!)\\
\writeline\writeline\writeline
\end{practicebox}

\end{document}
