%! AP Statistics — Unit 3, Lesson 3.6 — Homework
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

\begin{document}

\pageheader{Unit 3, Lesson 3.6}{Homework}
\namedateperiod

\vspace{0.1in}

\begin{practicebox}
\small
For each scenario, (a) recommend a design, (b) justify your choice, and
(c) draw a diagram.

\vspace{8pt}
\textbf{1.} A psychologist tests whether mindfulness training reduces anxiety in college
students. She has 40 students; she knows men and women may respond differently.

\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=8pt]
  \item Recommended design: \blank{7cm}
  \item Justify: \writeline\\[1pt]\writeline
  \item Draw a diagram:
  \vspace{1.3in}
\end{enumerate}

\vspace{8pt}
\textbf{2.} A dentist wants to compare two toothpaste brands for whitening. Each
patient has many teeth; they use Brand A on one side and Brand B on the other (randomly
assigned by coin flip).

\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=8pt]
  \item Recommended design: \blank{7cm}
  \item Why is this the most appropriate design? \writeline\\[1pt]\writeline
\end{enumerate}

\vspace{8pt}
\textbf{3.} A biologist tests whether a new growth hormone increases plant height. She
has 36 seedlings, all from the same variety and grown in the same conditions.

\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=8pt]
  \item Recommended design: \blank{7cm}
  \item Why is blocking not needed here? \writeline\\[1pt]\writeline
\end{enumerate}

\vspace{8pt}
\textbf{4.} Reflection: When is a CRD preferable to a block design, even if you know
a variable that affects the response?\\[4pt]
\writeline\\[1pt]\writeline\\[1pt]\writeline
\end{practicebox}

\end{document}
