%! AP Statistics — Unit 7, Lesson 7.1 — Warm-Up
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}
\newcommand{\TallMath}[1]{$\displaystyle #1\rule[-1.4em]{0pt}{3.2em}$}

\begin{document}

\pageheader{Unit 7, Lesson 7.1}{Warm-Up}
\namedateperiod

\vspace{0.15in}

A researcher conducts a study to determine whether the mean daily screen time for
teenagers differs from 7 hours. She takes a random sample of 40 teenagers and finds
$\bar x = 7.6$ hours with $s = 1.4$ hours.

\begin{enumerate}
  \item From Unit 5, describe the sampling distribution of $\bar x$ (assuming the
        population is approximately normal). Include shape, center, and standard deviation.

        \begin{itemize}
          \item \textbf{Shape:} \blank{7cm}
          \item \textbf{Center:} $\mu_{\bar x} = $ \blank{3cm}
          \item \textbf{Spread:} $\sigma_{\bar x} = \sigma/\sqrt{n} \approx s/\sqrt{n} = $ \blank{4cm}
        \end{itemize}

        \vspace{0.05in}

  \item The researcher tests $H_0{:}\ \mu = 7$ vs.\ $H_a{:}\ \mu \ne 7$ at $\alpha = 0.05$.
        She rejects $H_0$.

        \begin{enumerate}[label=\alph*.]
          \item If the true mean daily screen time is actually 7 hours, what type of
                error did the researcher commit? Circle your answer: \quad \textbf{Type I} \quad
                \textbf{Type II} \quad \textbf{No error}

                \vspace{0.05in}
          \item What is the probability that the researcher commits this type of error,
                assuming the test was conducted correctly? \blank{3cm}
        \end{enumerate}

        \vspace{0.05in}

  \item Suppose instead the researcher \emph{fails to reject} $H_0$, but the true
        mean screen time is actually 8 hours.

        \begin{enumerate}[label=\alph*.]
          \item What type of error has the researcher committed? Circle your answer:
                \quad \textbf{Type I} \quad \textbf{Type II} \quad \textbf{No error}

                \vspace{0.05in}
          \item In Unit 7 we will study procedures for \emph{means} using the
                $t$-distribution. Write one question you have about how errors in
                inference for means differ from errors in inference for proportions.

                \writelines{2}
        \end{enumerate}
\end{enumerate}

\end{document}
