%! AP Statistics — Unit 8, Lesson 8.5 — Homework
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}
\newcommand{\TallMath}[1]{$\displaystyle #1\rule[-1.4em]{0pt}{3.2em}$}

\begin{document}

\pageheader{Unit 8, Lesson 8.5}{Homework}
\namedateperiod

\vspace{0.1in}

\begin{enumerate}

  \item For each scenario below, \textbf{(i)} identify whether the appropriate test is a
        chi-square test for homogeneity or independence, \textbf{(ii)} explain your reasoning
        based on the study design, and \textbf{(iii)} write $H_0$ and $H_a$ in context.

        \begin{enumerate}[label=(\alph*)]

          \item Three brands of coffee (Brand X, Y, Z) each recruited a random sample of
                50 coffee tasters who rated their experience as Prefer, Neutral, or Dislike.

                Test type: \blank{4cm} \quad Reason: \writeline

                $H_0$: \writeline
                $H_a$: \writeline

                \vspace{0.06in}

          \item A simple random sample of 400 shoppers is asked their age group (18--30,
                31--50, or 51+) and their preferred shopping method (In-store, Online, or Both).

                Test type: \blank{4cm} \quad Reason: \writeline

                $H_0$: \writeline
                $H_a$: \writeline

                \vspace{0.06in}

          \item A simple random sample of 200 high school athletes is classified by sport
                (Football, Basketball, or Soccer) and GPA level (3.0 and above, or Below 3.0).

                Test type: \blank{4cm} \quad Reason: \writeline

                $H_0$: \writeline
                $H_a$: \writeline

        \end{enumerate}

  \item A student says scenarios (b) and (c) in Problem 1 both involve two categorical
        variables, so both must be tests for independence. Is the student correct?
        Explain your reasoning.

        \writelines{4}

  \item A researcher randomly selects 50 students from each of 3 schools
        (School P, Q, R) and asks each student which after-school program they prefer
        (Academic Support, Sports, or Arts). Total $n = 150$.

        \begin{enumerate}[label=(\alph*)]
          \item Identify the test type and write the hypotheses.

                \writelines{3}

          \item Write out the two conditions for this chi-square test.
                Can either condition be verified without seeing the actual data table?
                Explain.

                \writelines{4}
        \end{enumerate}

  \item \textbf{AP-Style Multiple Choice.} Which of the following scenarios calls for
        a chi-square test for \textbf{homogeneity}?

        \begin{enumerate}[label=(\Alph*)]
          \item A random sample of 500 adults is asked their employment status
                (Employed/Unemployed) and their level of financial stress (Low/Medium/High).
          \item Researchers randomly select 80 men and 80 women and record each person's
                preferred exercise type (Cardio/Strength/Flexibility).
          \item A random sample of 200 teenagers is asked their screen-time category
                ($<$2 hrs/$2$--$4$ hrs/$>$4 hrs/day) and their sleep quality (Good/Poor).
          \item A SRS of 300 patients from one hospital is classified by diagnosis
                (Diabetes/Hypertension/Neither) and insurance type (Private/Public/None).
        \end{enumerate}

\end{enumerate}

\begin{reflectionbox}
In your own words, what is the single most important question to ask when deciding whether
to use a chi-square test for homogeneity or independence? Write 1--2 sentences.
\writelines{3}
\end{reflectionbox}

\end{document}
