%! AP Statistics — Unit 1, Lesson 1.1 — Group Activity KEY
\documentclass[10pt]{article}
\usepackage[margin=0.65in, top=0.55in, bottom=0.65in]{geometry}
\usepackage{xcolor}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{array}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{colortbl}
\tcbuselibrary{breakable, skins}

% ── Colors ───────────────────────────────────────────────────────────────────
\definecolor{navy}{HTML}{1F3A5F}
\definecolor{navylight}{HTML}{2E5490}
\definecolor{sky}{HTML}{EAF3FB}
\definecolor{skymid}{HTML}{C5DFF5}
\definecolor{goldacc}{HTML}{D4820A}
\definecolor{goldbg}{HTML}{FEF3E2}
\definecolor{greenbg}{HTML}{EDF8F0}
\definecolor{greenacc}{HTML}{2D7A4F}
\definecolor{redbg}{HTML}{FCECEC}
\definecolor{redacc}{HTML}{C0392B}
\definecolor{charcoal}{HTML}{2C3E50}
\definecolor{slate}{HTML}{64748B}
\definecolor{linegray}{HTML}{AAAAAA}
\definecolor{keyred}{HTML}{C0392B}

% ── Box styles ───────────────────────────────────────────────────────────────
\newtcolorbox{scenariobox}[2][]{
    enhanced,
    colback=white, colframe=#2, boxrule=0.9pt, arc=2mm,
    left=3mm, right=3mm, top=2mm, bottom=4mm,
    fonttitle=\bfseries\small\color{white}, title={#1},
    attach boxed title to top left={yshift=-2mm, xshift=4mm},
    boxed title style={colback=#2, colframe=#2, arc=1.5mm},
    breakable
}
\newtcolorbox{headlinebox}[1]{
    enhanced,
    colback=#1, colframe=#1!60!black, boxrule=0pt,
    arc=1.5mm, left=3mm, right=3mm, top=2mm, bottom=2mm
}
\newtcolorbox{teachernote}{
    enhanced,
    colback=redbg, colframe=redacc, boxrule=0.7pt, arc=1.5mm,
    left=2mm, right=2mm, top=1.5mm, bottom=1.5mm,
    fonttitle=\bfseries\scriptsize\color{white}, title={Teacher Note},
    attach boxed title to top left={yshift=-2mm, xshift=4mm},
    boxed title style={colback=redacc, colframe=redacc, arc=1mm}
}

% ── Fill-in helpers ──────────────────────────────────────────────────────────
\newcommand{\ans}[1]{\textcolor{keyred}{\textit{#1}}}
\newcommand{\writeline}{\vspace{1pt}\noindent\textcolor{linegray}{\hrulefill}\vspace{3pt}}

% ── Component table (key version) ────────────────────────────────────────────
\newcommand{\componenttablekey}[4]{%
\renewcommand{\arraystretch}{1.8}
\begin{tabularx}{\linewidth}{@{} >{\bfseries\color{navy}}p{0.22\linewidth} X @{}}
Individual:  & \ans{#1} \\
Population:  & \ans{#2} \\
Sample:      & \ans{#3} \\
Variable(s): & \ans{#4} \\
\end{tabularx}}

% ── List / para settings ─────────────────────────────────────────────────────
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}

%=============================================================================
\begin{document}

% ── Page header ──────────────────────────────────────────────────────────────
    \noindent
    \colorbox{navy}{%
        \parbox{\dimexpr\linewidth}{%
            \vspace{6pt}
            \color{white}\textbf{\large AP Statistics \hfill Unit 1, Lesson 1.1}\\[2pt]
            {\color{skymid}\small\textbf{Group Activity}}
            \vspace{6pt}
        }%
    }
    \vspace{1.5em}

\noindent
\begin{tabularx}{\linewidth}{X X X}
Name:\;\textcolor{keyred}{\textit{Key}} & Partner:\; & Period:\;
\end{tabularx}

\vspace{0.1in}

\begin{tcolorbox}[colback=sky, colframe=navy, boxrule=0.8pt, arc=2mm,
    left=3mm, right=3mm, top=2mm, bottom=2mm]
\small
For each headline below, identify the \textbf{individual}, \textbf{population},
\textbf{sample}, and \textbf{variable(s)}. Then answer the follow-up question.
Remember: the \emph{population} is who or what we \emph{want} to know about;
the \emph{sample} is who or what we \emph{actually studied}.
\end{tcolorbox}

\vspace{0.14in}

% ════════════════════════════════════════════════════════════════════════════
% SCENARIO 1 KEY
% ════════════════════════════════════════════════════════════════════════════
\begin{scenariobox}[Scenario 1]{navylight}

\begin{headlinebox}{sky}
\small\textit{``A survey of 500 U.S.\ high school students found that 78\% report
feeling stressed about grades at least once a week.''}
\end{headlinebox}

\vspace{8pt}
\componenttablekey
  {A U.S.\ high school student}
  {All U.S.\ high school students}
  {The 500 students surveyed}
  {How often the student feels stressed about grades (categorical / ordinal)}

\vspace{8pt}
\small\textbf{Would it be possible to conduct a census for this study?}\\[4pt]
\ans{No --- there are roughly 15 million high school students in the U.S.
Surveying all of them would be impossible due to cost, time, and logistics.
A well-chosen sample of 500 can still give reliable results.}

\end{scenariobox}

\vspace{0.12in}

% ════════════════════════════════════════════════════════════════════════════
% SCENARIO 2 KEY
% ════════════════════════════════════════════════════════════════════════════
\begin{scenariobox}[Scenario 2]{greenacc}

\begin{headlinebox}{greenbg}
\small\textit{``A national study tracked 1{,}200 elementary school students over
three years and found that those who had at least 30 minutes of recess daily
scored higher on standardized reading assessments.''}
\end{headlinebox}

\vspace{8pt}
\componenttablekey
  {An elementary school student}
  {All U.S.\ elementary school students (accept: all elementary school students)}
  {The 1{,}200 students tracked in the study}
  {Daily recess time (quantitative); score on standardized reading assessment (quantitative)}

\vspace{6pt}
\begin{teachernote}
\scriptsize
Students may define the population too narrowly (``students in this study'') or too broadly
(``all children in the world''). Push them to use the headline's scope --- ``national study''
implies U.S.\ students. Also worth noting: two variables are present; students who identify
only one are partially correct --- ask them what else was measured.
\end{teachernote}

\vspace{8pt}
\small\textbf{Does association mean causation?}\\[4pt]
\ans{No. The study shows that more recess \emph{goes along with} higher reading scores,
but there could be other explanations --- for example, schools that offer more recess
might also have better-funded programs overall, or students who get more exercise may
simply be more alert. To establish causation we would need a controlled experiment.}

\end{scenariobox}

\vspace{0.12in}

% ════════════════════════════════════════════════════════════════════════════
% SCENARIO 3 KEY
% ════════════════════════════════════════════════════════════════════════════
\begin{scenariobox}[Scenario 3 \normalfont\small\color{white!80!black}\quad stretch]{redacc}

\begin{headlinebox}{redbg}
\small\textit{``Scientists examined 60 coral reef sites across the Pacific Ocean
and found that water temperature had increased at 85\% of them over the past decade.''}
\end{headlinebox}

\vspace{8pt}
\componenttablekey
  {A coral reef site (not a person --- a location)}
  {All coral reef sites in the Pacific Ocean}
  {The 60 reef sites examined}
  {Water temperature change over the past decade (quantitative)}

\vspace{6pt}
\begin{teachernote}
\scriptsize
The most common error here is writing ``a scientist'' or ``the ocean'' as the individual.
Emphasize: the individual is whatever the researchers recorded data \emph{about} --- here,
each measurement belongs to a reef site. This is a high-value AP misconception to address early.
Population boundary is also genuinely ambiguous (Pacific only? all oceans?); accept either
as long as students justify their choice.
\end{teachernote}

\vspace{8pt}
\small\textbf{``The individual is the ocean.'' Do you agree?}\\[4pt]
\ans{No. The individual is a \emph{coral reef site} --- a specific, measurable location.
The ocean is the broader context, not the unit being observed. Each data point in the study
belongs to one reef site: its name (or coordinates) and its recorded temperature change.
The ocean as a whole was never measured as a single entity.}

\end{scenariobox}

\vspace{0.12in}

% ── Reflection ───────────────────────────────────────────────────────────────
\begin{tcolorbox}[colback=goldbg, colframe=goldacc, boxrule=0.8pt, arc=2mm,
    left=3mm, right=3mm, top=2mm, bottom=2mm]
\small\textbf{Reflection:} \quad Which scenario was hardest? What made it harder?\\[4pt]
\ans{Most students will say Scenario 3. The key difficulty is that the individual is not a
person --- it requires stepping back and asking ``what was each measurement \emph{about}?''
rather than ``who was in the study?'' This is exactly the habit AP free-response rewards.}
\end{tcolorbox}

\end{document}
