%! AP Statistics — Unit 5, Lesson 5.3 — Group Activity
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

\begin{document}

\pageheader{Unit 5, Lesson 5.3}{Group Activity}
\namepartnerperiod

\vspace{0.1in}

\begin{tcolorbox}[colback=redbg, colframe=black!40, boxrule=0.6pt, arc=2mm,
    left=3mm, right=3mm, top=2mm, bottom=2mm, title=\textbf{Tier R --- Remediate}]
\textbf{Context: Granola bar weights.}
A factory produces granola bars with $\mu = 45$ g and $\sigma = 4$ g.
A quality inspector randomly selects $n = 16$ bars each hour.

\begin{enumerate}
  \item Check the three conditions for using the normal model for $\bar{x}$. State whether
        each is met and why.
        \writelines{4}
  \item Find $\mu_{\bar{x}}$ and $\sigma_{\bar{x}}$.
        \vspace{0.6in}
  \item What is the probability that the inspector's sample mean weight is between 43 g
        and 47 g? (The population is approximately normal.)
        \vspace{1.0in}
\end{enumerate}
\end{tcolorbox}

\vspace{0.15in}

\begin{tcolorbox}[colback=redbg, colframe=black!40, boxrule=0.6pt, arc=2mm,
    left=3mm, right=3mm, top=2mm, bottom=2mm, title=\textbf{Tier A --- Approaching Proficiency}]
\textbf{Context: Commute times.}
Commute times in a large city are right-skewed with $\mu = 32$ min and $\sigma = 11$ min.
A researcher surveys $n = 50$ randomly selected commuters.

\begin{enumerate}
  \item Check all three conditions. Is it appropriate to model $\bar{x}$ as normal?
        \writelines{3}
  \item Compute $\mu_{\bar{x}}$ and $\sigma_{\bar{x}}$.
        \vspace{0.5in}
  \item Find $P(\bar{x} > 35)$.
        \vspace{1.0in}
  \item Find the value $c$ such that $P(\bar{x} < c) = 0.10$. Interpret in context.
        \vspace{1.0in}
\end{enumerate}
\end{tcolorbox}

\vspace{0.15in}

\begin{tcolorbox}[colback=redbg, colframe=black!40, boxrule=0.6pt, arc=2mm,
    left=3mm, right=3mm, top=2mm, bottom=2mm, title=\textbf{Tier E --- Extension}]
\textbf{Context: ATM withdrawal amounts.}
ATM withdrawals at a campus ATM are right-skewed with $\mu = \$65$ and $\sigma = \$30$.

\begin{enumerate}
  \item For $n = 9$: can we use the normal model for $\bar{x}$? Explain.
        \writelines{2}
  \item For $n = 64$: compute $\mu_{\bar{x}}$, $\sigma_{\bar{x}}$, and $P(\bar{x} > 70)$.
        \vspace{1.0in}
  \item How large must $n$ be for $\sigma_{\bar{x}} \le \$3$? Show work.
        \vspace{0.8in}
  \item A bank manager claims: ``If we take enough samples, the individual withdrawal amounts
        will become normally distributed.'' Is this claim correct? Explain.
        \writelines{3}
\end{enumerate}
\end{tcolorbox}

\end{document}
