%! AP Statistics — Unit 2, Lesson 2.4 — Exit Ticket (Answer Key)
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-key}

%=============================================================================
\begin{document}

\pageheader{Unit 2, Lesson 2.4}{Exit Ticket --- Answer Key}
\namedateperiod

\vspace{0.22in}

\begin{tcolorbox}[colback=sky, colframe=navy, boxrule=0.9pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small\textit{A researcher recorded the number of hours of television watched per day and
the GPA for a sample of 25 high school students. The scatterplot below shows the data.}

\vspace{8pt}
\begin{center}
\begin{tikzpicture}[scale=0.9]
  \draw[very thin, gray!35] (0,0) grid[xstep=0.5, ystep=0.5] (7, 5);
  \draw[->, thick, navy] (0,0) -- (7.4,0)
        node[right, font=\small, navy] {TV (hr/day)};
  \draw[->, thick, navy] (0,0) -- (0,5.5)
        node[above, font=\small, navy] {GPA};
  \foreach \x in {0,1,...,7}
    \node[below, font=\scriptsize] at (\x,0) {\x};
  \foreach \y/\lbl in {0/1.0, 1/1.5, 2/2.0, 3/2.5, 4/3.0, 5/3.5}
    \node[left, font=\scriptsize] at (0,\y) {\lbl};
  \filldraw[navy!70] (0.5,4.8) circle (2.2pt);
  \filldraw[navy!70] (1,4.2) circle (2.2pt);
  \filldraw[navy!70] (1,4.5) circle (2.2pt);
  \filldraw[navy!70] (1.5,3.8) circle (2.2pt);
  \filldraw[navy!70] (1.5,4.0) circle (2.2pt);
  \filldraw[navy!70] (2,3.5) circle (2.2pt);
  \filldraw[navy!70] (2,3.2) circle (2.2pt);
  \filldraw[navy!70] (2.5,3.0) circle (2.2pt);
  \filldraw[navy!70] (2.5,2.8) circle (2.2pt);
  \filldraw[navy!70] (3,2.5) circle (2.2pt);
  \filldraw[navy!70] (3,2.2) circle (2.2pt);
  \filldraw[navy!70] (3.5,2.0) circle (2.2pt);
  \filldraw[navy!70] (3.5,2.4) circle (2.2pt);
  \filldraw[navy!70] (4,1.8) circle (2.2pt);
  \filldraw[navy!70] (4,2.0) circle (2.2pt);
  \filldraw[navy!70] (4.5,1.5) circle (2.2pt);
  \filldraw[navy!70] (4.5,1.8) circle (2.2pt);
  \filldraw[navy!70] (5,1.3) circle (2.2pt);
  \filldraw[navy!70] (5,1.5) circle (2.2pt);
  \filldraw[navy!70] (5.5,1.2) circle (2.2pt);
  \filldraw[navy!70] (5.5,1.0) circle (2.2pt);
  \filldraw[navy!70] (6,0.8) circle (2.2pt);
  \filldraw[navy!70] (6,1.0) circle (2.2pt);
  \filldraw[navy!70] (6.5,0.8) circle (2.2pt);
  \filldraw[redacc] (7,4.6) circle (2.8pt);
\end{tikzpicture}
\end{center}
\end{tcolorbox}

\vspace{0.2in}

\begin{enumerate}[leftmargin=1.6em, itemsep=0.2in]

    \item Identify the explanatory and response variables for this scatterplot.\\[10pt]
          Explanatory: \ans{daily TV hours} \quad Response: \ans{GPA}

    \item Write a \textbf{complete DOFS description} of the association shown in the scatterplot.
          Include direction, form, strength, and any outlier(s) --- all in context.\\[10pt]
          \ansline{There is a moderate negative linear association between daily TV hours and GPA}\\[3pt]
          \ansline{for these 25 students. As daily TV hours increase, GPA tends to decrease.}\\[3pt]
          \ansline{There is one outlier: a student who watches about 7 hours of TV daily but has a}\\[3pt]
          \ansline{GPA of approximately 3.8, which is much higher than the pattern would suggest.}

    \item The red point (far right) represents one student. Describe this point in context.
          Is it an outlier? Explain.\\[10pt]
          \ansline{Yes, it is an outlier. This student watches approximately 7 hr/day of TV but has}\\[3pt]
          \ansline{a GPA near 3.8 --- far above what the overall pattern predicts for that level of}\\[3pt]
          \ansline{TV watching. It deviates clearly from the downward linear pattern.}

\end{enumerate}

\vspace{0.16in}

\begin{tcolorbox}[colback=redbg, colframe=redacc, boxrule=0.8pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small\textbf{AP-Style Practice}\\[6pt]
A scatterplot of $x$ vs.\ $y$ shows points that are tightly clustered along a line sloping
downward from left to right, with one point far above the line at the right edge. Which of the
following best describes this scatterplot?

\vspace{10pt}
\begin{enumerate}[label=\textbf{(\Alph*)}, leftmargin=2em, itemsep=6pt]
  \item Strong positive linear association with no outliers
  \item Strong negative linear association with no outliers
  \item Moderate negative linear association with no outliers
  \item Strong negative linear association with one outlier \textcolor{keyred}{\textbf{$\leftarrow$ correct}}
\end{enumerate}
\end{tcolorbox}

\begin{teachernote}
(A) Wrong direction; (B) ignores the outlier; (C) ``moderate'' contradicts ``tightly clustered.''
(D) is correct: tightly clustered = strong, sloping downward = negative, one point far above = outlier.
\end{teachernote}

\vspace{0.1in}
\noindent\textcolor{slate}{\small My answer: \ans{D} \quad Because: \ans{strong (tight), negative (down-right slope), one outlier above the pattern}}

\end{document}
