%! AP Statistics — Unit 1, Lesson 1.1 — Student Packet Cover Sheet
\documentclass[10pt]{article}
\usepackage[margin=0.65in, top=0.55in, bottom=0.65in]{geometry}
\usepackage{xcolor}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{array}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{colortbl}
\usepackage{booktabs}
\tcbuselibrary{breakable, skins}

% ── Colors ──────────────────────────────────────────────────────────────────
\definecolor{navy}{HTML}{1F3A5F}
\definecolor{navylight}{HTML}{2E5490}
\definecolor{sky}{HTML}{EAF3FB}
\definecolor{skymid}{HTML}{C5DFF5}
\definecolor{goldacc}{HTML}{D4820A}
\definecolor{goldbg}{HTML}{FEF3E2}
\definecolor{greenbg}{HTML}{EDF8F0}
\definecolor{greenacc}{HTML}{2D7A4F}
\definecolor{charcoal}{HTML}{2C3E50}
\definecolor{slate}{HTML}{64748B}
\definecolor{linegray}{HTML}{AAAAAA}

% ── Box styles ───────────────────────────────────────────────────────────────
\newtcolorbox{objectivebox}{
    enhanced,
    colback=sky, colframe=navy, boxrule=1pt, arc=2mm,
    left=3mm, right=3mm, top=2mm, bottom=2mm,
    fonttitle=\bfseries\small\color{white},
    title={Learning Targets — I Can\dots},
    attach boxed title to top left={yshift=-2mm, xshift=4mm},
    boxed title style={colback=navy, colframe=navy, arc=1.5mm}
}
\newtcolorbox{vocabbox}{
    enhanced,
    colback=greenbg, colframe=greenacc, boxrule=0.8pt, arc=2mm,
    left=3mm, right=3mm, top=2mm, bottom=2mm,
    fonttitle=\bfseries\small\color{white}, title={Vocabulary},
    attach boxed title to top left={yshift=-2mm, xshift=4mm},
    boxed title style={colback=greenacc, colframe=greenacc, arc=1.5mm},
    breakable
}
\newtcolorbox{tocbox}{
    enhanced,
    colback=white, colframe=navy, boxrule=0.8pt, arc=2mm,
    left=3mm, right=3mm, top=2mm, bottom=2mm,
    fonttitle=\bfseries\small\color{white}, title={What's in This Packet},
    attach boxed title to top left={yshift=-2mm, xshift=4mm},
    boxed title style={colback=navy, colframe=navy, arc=1.5mm}
}
\newtcolorbox{remindbox}{
    enhanced,
    colback=goldbg, colframe=goldacc, boxrule=0.8pt, arc=2mm,
    left=3mm, right=3mm, top=2mm, bottom=2mm,
    fonttitle=\bfseries\small\color{white}, title={Keep in Mind},
    attach boxed title to top left={yshift=-2mm, xshift=4mm},
    boxed title style={colback=goldacc, colframe=goldacc, arc=1.5mm}
}

% ── Fill-in helpers ──────────────────────────────────────────────────────────
\newcommand{\blank}[1]{\underline{\hspace{#1}}}

% ── List / para settings ─────────────────────────────────────────────────────
\setlist[itemize]{leftmargin=1.3em, itemsep=4pt, topsep=2pt}
\setlist[enumerate]{leftmargin=1.5em, itemsep=4pt, topsep=2pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}

%=============================================================================
\begin{document}

% ── Page header ──────────────────────────────────────────────────────────────
\begin{tikzpicture}[remember picture, overlay]
  \fill[navy] (current page.north west)
    rectangle ([yshift=-0.9in]current page.north east);
\end{tikzpicture}
\vspace{-0.8in}

\begin{center}
  {\color{white}\textbf{\LARGE AP Statistics}}\\[4pt]
  {\color{skymid}\large\textbf{Unit 1: Exploring One-Variable Data}}\\[6pt]
  {\color{white}\textbf{\large Lesson 1.1 \quad Introducing Statistics}}
\end{center}

\vspace{0.22in}

% Name / Date / Period row
\noindent
\begin{tabularx}{\linewidth}{X X X}
Name:\;\blank{4.8cm} & Date:\;\blank{2.8cm} & Period:\;\blank{1.5cm}
\end{tabularx}

\vspace{0.18in}

% ── LEARNING TARGETS ─────────────────────────────────────────────────────────
\begin{objectivebox}
\small
\begin{enumerate}[leftmargin=1.5em, itemsep=5pt]
  \item \ldots{} explain what statistics is and describe the 4-step statistical
        problem-solving process.
  \item \ldots{} identify the individual, population, sample, and variable(s)
        in a statistical scenario.
  \item \ldots{} explain why variation in data is the reason statistics is useful,
        and distinguish between a sample and a dataset.
\end{enumerate}
\end{objectivebox}

\vspace{0.14in}

% ── TABLE OF CONTENTS ────────────────────────────────────────────────────────
\begin{tocbox}
\small
\renewcommand{\arraystretch}{1.5}
\begin{tabularx}{\linewidth}{@{} c l X r @{}}
\rowcolor{sky}
\textbf{\#} & \textbf{Component} & \textbf{Description} & \textbf{Score} \\
\midrule
1 & Warm-Up       & Prior knowledge + class data collection   & \blank{1.2cm} \\
2 & Guided Notes  & Direct instruction notes \& key concepts   & \blank{1.2cm} \\
3 & Group Activity & Scenario analysis with your partner       & \blank{1.2cm} \\
4 & Exit Ticket   & Individual scenario identification (completeness) & \blank{1.2cm} \\
5 & Homework      & Real-world data identification + reflection & \blank{1.2cm} \\
\midrule
  & \multicolumn{2}{r}{\textbf{Total}} & \blank{1.2cm} \\
\end{tabularx}
\end{tocbox}


\vspace{0.14in}

% ── KEEP IN MIND ─────────────────────────────────────────────────────────────
\begin{remindbox}
\small
These ideas will come up again and again all year. Start building the habit of asking them now.

\vspace{6pt}
\begin{tabularx}{\linewidth}{@{} >{\centering\arraybackslash\columncolor{goldbg}}p{0.06\linewidth}
                                    X @{}}
\textbf{\large!} &
\textbf{Association $\neq$ Causation.}\enspace
A study can show that two things are related without proving one \emph{causes} the other. \\[6pt]
\textbf{\large!} &
\textbf{Sample $\neq$ Data.}\enspace
The sample is the set of \emph{individuals} selected. The data are the \emph{values recorded}
for those individuals. \\[6pt]
\textbf{\large!} &
\textbf{Variation is informative, not a problem.}\enspace
If every individual gave the same answer, we would not need statistics at all. \\[6pt]
\textbf{\large!} &
\textbf{The 4-step process spirals all year.}\enspace
Ask a question $\to$ Collect data $\to$ Analyze $\to$ Interpret. You will use this framework
in every unit. \\
\end{tabularx}
\end{remindbox}

\end{document}
