%! AP Statistics — Unit 1, Lesson 1.10 — Warm-Up
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

%=============================================================================
\begin{document}

\pageheader{Unit 1, Lesson 1.10}{Warm-Up}
\namedateperiod

\vspace{0.16in}

\noindent In Lesson 1.9 you compared distributions of two groups.
Today you will work with a specific model for symmetric, bell-shaped distributions.
The curve below shows the distribution of \textbf{heights of adult men} (inches),
which is approximately $N(70, 3)$. The shaded region highlights heights within
\textbf{one standard deviation of the mean}.

\vspace{0.18in}

\begin{center}
\begin{tikzpicture}[scale=1.0]
  % Shade region: z = -1 to 1
  \fill[sky, opacity=0.85]
    plot[domain=-1:1, samples=40] (\x, {2.5*exp(-\x*\x/2)})
    -- (1, 0) -- (-1, 0) -- cycle;
  % Bell curve
  \draw[thick, navy]
    plot[domain=-3.5:3.5, samples=80] (\x, {2.5*exp(-\x*\x/2)});
  % Axis
  \draw[thick] (-3.8, 0) -- (3.8, 0);
  % Vertical reference lines at z = -1, 0, 1
  \draw[dashed, charcoal] (-1, 0) -- (-1, {2.5*exp(-0.5)});
  \draw[dashed, charcoal] ( 1, 0) -- ( 1, {2.5*exp(-0.5)});
  % Tick marks and labels (height values below, z-scores above axis)
  \foreach \z/\h in {-3/61, -2/64, -1/67, 0/70, 1/73, 2/76, 3/79} {
    \draw (\z, -0.12) -- (\z, 0.12);
    \node[below, font=\small] at (\z, -0.15) {\h};
  }
  \node[below, font=\small\itshape] at (0, -0.55) {Height (inches)};
  % Mean label
  \node[above, font=\small\bfseries\color{navy}] at (0, 2.52) {$\mu = 70$};
\end{tikzpicture}
\end{center}

\vspace{0.20in}

\begin{enumerate}[leftmargin=1.5em, itemsep=10pt]

  \item What is the \textbf{mean} ($\mu$) and \textbf{standard deviation} ($\sigma$)
        of this distribution?\\[6pt]
        $\mu = \blank{2cm}$ inches \qquad $\sigma = \blank{2cm}$ inches

  \item The shaded region covers heights from 67 to 73 inches.
        How many standard deviations above and below the mean do these values lie?\\[6pt]
        $67 = \mu - \blank{1cm}\,\sigma$ \qquad $73 = \mu + \blank{1cm}\,\sigma$

  \item What percentage of men do you think fall in the shaded region?
        (Estimate before today's lesson.)\\[6pt]
        Estimate: \blank{3cm}\% \quad Reasoning: \blank{8cm}

  \item A man is 76 inches tall. Is his height above or below the mean?
        How many standard deviations away from the mean is he?\\[6pt]
        \writeline

\end{enumerate}

\vspace{0.14in}

\begin{tcolorbox}[colback=greenbg, colframe=greenacc, boxrule=0.8pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small
\begin{itemize}[leftmargin=1.3em, itemsep=5pt]
  \item Today you will learn the \textbf{Normal distribution} and its two parameters
        $\mu$ (mean) and $\sigma$ (standard deviation).
  \item You will apply the \textbf{68--95--99.7 Rule} to find approximate proportions
        without a table.
  \item You will calculate \textbf{$z$-scores} and use the Normal table to find
        precise probabilities and percentiles.
\end{itemize}
\end{tcolorbox}

\vspace{0.12in}

\noindent\textcolor{slate}{\small One question you have going into today's lesson,
or something you're not sure about yet:}\\[8pt]
\writeline

\end{document}
