%! AP Statistics — Unit 2, Lesson 2.2 — Exit Ticket
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

%=============================================================================
\begin{document}

\pageheader{Unit 2, Lesson 2.2}{Exit Ticket}
\namedateperiod

\vspace{0.22in}

% ── SCENARIO ─────────────────────────────────────────────────────────────────
\begin{tcolorbox}[colback=sky, colframe=navy, boxrule=0.9pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small\textit{A researcher surveyed 180 students about whether they own a pet (Yes/No)
and whether they volunteer in their community (Yes/No). The results are partially
shown below.}

\vspace{10pt}
\renewcommand{\arraystretch}{1.9}
\begin{tabularx}{\linewidth}{@{} l C{2.6cm} C{2.6cm} C{2.4cm} @{}}
\rowcolor{sky}
                    & \textbf{Volunteer: Yes} & \textbf{Volunteer: No} & \textbf{Row Total} \\
\hline
\textbf{Pet: Yes}   & 48 & 72 & \blank{1.8cm} \\
\textbf{Pet: No}    & 24 & 36 & \blank{1.8cm} \\
\hline
\textbf{Col.\ Total}& \blank{1.8cm} & \blank{1.8cm} & \blank{1.8cm} \\
\end{tabularx}
\end{tcolorbox}

\vspace{0.18in}

\begin{enumerate}[leftmargin=1.6em, itemsep=0.18in]

    \item Fill in all missing row totals, column totals, and the grand total
          in the table above.

    \item Compute the conditional relative frequency of volunteering for each
          pet-ownership group. Show your work.\\[6pt]
          P(Volunteer $|$ Pet: Yes) $= \dfrac{\blank{1.2cm}}{\blank{1.2cm}} = \blank{2cm}$
          \hfill
          P(Volunteer $|$ Pet: No) $= \dfrac{\blank{1.2cm}}{\blank{1.2cm}} = \blank{2cm}$

    \item Is there evidence of an association between pet ownership and volunteering?
          Circle: \quad \textbf{Yes} \quad / \quad \textbf{No}\\[8pt]
          Justify using the values you computed in \#2:\\[6pt]
          \writeline\\[1pt]\writeline\\[1pt]\writeline

\end{enumerate}

\vspace{0.2in}

% ── AP-STYLE MC ──────────────────────────────────────────────────────────────
\begin{tcolorbox}[colback=redbg, colframe=redacc, boxrule=0.8pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small\textbf{AP-Style Practice}\\[6pt]
A two-way table shows grade level (9th/10th) and extracurricular participation
(Yes/No). For 9th graders, 60\% participate; for 10th graders, 55\% participate.
Which statement best describes the relationship?

\vspace{10pt}
\begin{enumerate}[label=\textbf{(\Alph*)}, leftmargin=2em, itemsep=6pt]
  \item There is no association because both values are below 100\%.
  \item There is a strong positive association because more than half participate in both groups.
  \item There is weak or no association because the conditional distributions are nearly the same.
  \item Association cannot be determined without the actual cell counts.
\end{enumerate}
\end{tcolorbox}

\vspace{0.12in}
\noindent\textcolor{slate}{\small My answer: \blank{1cm} \quad Because: \blank{8.5cm}}

\end{document}
