%! AP Statistics — Unit 2, Lesson 2.1 — Exit Ticket
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

%=============================================================================
\begin{document}

\pageheader{Unit 2, Lesson 2.1}{Exit Ticket}
\namedateperiod

\vspace{0.22in}

% ── SCENARIO ─────────────────────────────────────────────────────────────────
\begin{tcolorbox}[colback=sky, colframe=navy, boxrule=0.9pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small\textit{A researcher surveys 30 high school students and finds that students
who drink more coffee (in cups per week) tend to have higher GPAs.}
\end{tcolorbox}

\vspace{0.2in}

\textbf{Answer the questions below for the scenario above.}
\textcolor{slate}{\small Write in complete phrases --- one sentence is enough for each.}

\vspace{0.16in}

\renewcommand{\arraystretch}{2.4}
\begin{tabularx}{\linewidth}{@{} >{\bfseries\color{navy}}p{0.32\linewidth} X @{}}
Two variables:           & \blank{9cm} \\
Variable types:          & \blank{9cm} \\
Could this be random?    & \blank{9cm} \\
One confounding variable: & \blank{9cm} \\
\end{tabularx}

\vspace{0.22in}

\textbf{Does this study prove that drinking coffee causes higher grades? Explain.}\\[8pt]
\writeline\\[2pt]\writeline\\[2pt]\writeline

\vspace{0.24in}

% ── AP-STYLE MC ──────────────────────────────────────────────────────────────
\begin{tcolorbox}[colback=redbg, colframe=redacc, boxrule=0.8pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small\textbf{AP-Style Practice}\\[6pt]
A study found a strong positive association between the number of fire trucks sent to
a fire and the amount of property damage. Which of the following is the most plausible
explanation for this association?

\vspace{10pt}
\begin{enumerate}[label=\textbf{(\Alph*)}, leftmargin=2em, itemsep=6pt]
  \item Fire trucks cause property damage.
  \item Property damage attracts more fire trucks.
  \item The size of the fire is a confounding variable.
  \item The association is probably random because no experiment was conducted.
\end{enumerate}
\end{tcolorbox}

\vspace{0.12in}
\noindent\textcolor{slate}{\small My answer: \blank{1cm} \quad Because: \blank{8.5cm}}

\end{document}
