%! AP Statistics — Unit 3, Lesson 3.1 — Student Guided Notes
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

\begin{document}

\pageheader{Unit 3, Lesson 3.1}{Guided Notes}
\namedateperiod

\vspace{0.12in}

\begin{objectivebox}
\small By the end of this lesson, I will be able to\dots\\[4pt]
\writeline\\[1pt]
\writeline\\[1pt]
\writeline
\end{objectivebox}

\vspace{0.1in}

\begin{vocabbox}
\termblanklong{Data collection method}
\termblanklong{Chance-based method}
\termblanklong{Non-chance method}
\termblanklong{Bias}
\termblanklong{Anecdotal evidence}
\end{vocabbox}

\vspace{0.1in}

\begin{hookbox}
\small\textbf{Three surveys:}
\begin{enumerate}[leftmargin=1.5em, itemsep=4pt]
  \item A grocery store comment card near the exit: 12 responses, all complaints.
  \item A news website polls online visitors about a school bond.
  \item A researcher randomly dials 400 phone numbers.
\end{enumerate}
\textbf{Which would you trust most? Why?}\\[4pt]
\writeline\\[1pt]\writeline
\end{hookbox}

\vspace{0.1in}

\begin{notesbox}{The Trustworthiness of Data}
\small
\textbf{Key Principle (VAR-1.E.1):} Methods for data collection that do \textbf{not}
rely on \blank{3cm} result in \blank{3cm} conclusions.

\vspace{10pt}
\renewcommand{\arraystretch}{1.6}
\begin{tabularx}{\linewidth}{@{} >{\bfseries\color{navy}}p{0.3\linewidth} X @{}}
Chance-based method & \blank{8cm} \\
Non-chance method & \blank{8cm} \\
\end{tabularx}

\vspace{10pt}
\textbf{Counter-intuitive fact:} A \blank{3cm} non-random sample is \textbf{not} more
trustworthy than a \blank{3cm} random sample.

\vspace{8pt}
\textbf{The 1936 Literary Digest Poll:}
\begin{itemize}[itemsep=2pt]
  \item Contacted \blank{2cm} people --- one of the largest polls ever.
  \item Predicted \blank{4cm} would win the presidential election.
  \item Actual winner: \blank{4cm}
  \item Why it failed: \blank{7cm}
\end{itemize}
\end{notesbox}

\vspace{0.1in}

\begin{notesbox}{Evaluating a Data Collection Method}
\small
For any data collection scenario, ask these questions:

\vspace{6pt}
\renewcommand{\arraystretch}{1.8}
\begin{tabularx}{\linewidth}{@{} l X @{}}
\textbf{Question} & \textbf{My answer} \\
\hline
Was chance used to select individuals? & \blank{8cm} \\
Whose opinions/data are represented? & \blank{8cm} \\
Who is \emph{not} represented? & \blank{8cm} \\
Can conclusions be trusted for the whole population? & \blank{8cm} \\
\end{tabularx}
\end{notesbox}

\vspace{0.1in}

\begin{practicebox}
\small Classify each as more trustworthy (\checkmark) or less trustworthy ($\times$).
Explain your reasoning in one phrase.

\vspace{6pt}
\begin{enumerate}[leftmargin=1.5em, itemsep=10pt]
  \item A radio station invites listeners to text in their opinion about a new law.
        \blank{1cm} \quad \blank{9cm}

  \item A researcher uses a random number table to select 200 voters from the
        registered voter list. \blank{1cm} \quad \blank{8cm}

  \item A teacher surveys her own class to find out how all students in the school
        feel about homework. \blank{1cm} \quad \blank{7cm}
\end{enumerate}
\end{practicebox}

\end{document}
