%! AP Statistics — Unit 1, Lesson 1.1 — Group Activity
\documentclass[10pt]{article}
\usepackage[margin=0.65in, top=0.55in, bottom=0.65in]{geometry}
\usepackage{xcolor}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{array}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{colortbl}
\tcbuselibrary{breakable, skins}

% ── Colors ───────────────────────────────────────────────────────────────────
\definecolor{navy}{HTML}{1F3A5F}
\definecolor{navylight}{HTML}{2E5490}
\definecolor{sky}{HTML}{EAF3FB}
\definecolor{skymid}{HTML}{C5DFF5}
\definecolor{goldacc}{HTML}{D4820A}
\definecolor{goldbg}{HTML}{FEF3E2}
\definecolor{greenbg}{HTML}{EDF8F0}
\definecolor{greenacc}{HTML}{2D7A4F}
\definecolor{redbg}{HTML}{FCECEC}
\definecolor{redacc}{HTML}{C0392B}
\definecolor{charcoal}{HTML}{2C3E50}
\definecolor{slate}{HTML}{64748B}
\definecolor{linegray}{HTML}{AAAAAA}

% ── Box styles ───────────────────────────────────────────────────────────────
\newtcolorbox{scenariobox}[2][]{
    colback=white, colframe=#2, boxrule=0.9pt, arc=2mm,
    left=3mm, right=3mm, top=2mm, bottom=4mm,
    fonttitle=\bfseries\small\color{white}, title={#1},
    attach boxed title to top left={yshift=-2mm, xshift=4mm},
    boxed title style={colback=#2, colframe=#2, arc=1.5mm},
    breakable
}
\newtcolorbox{headlinebox}[1]{
    colback=#1, colframe=#1!60!black, boxrule=0pt,
    arc=1.5mm, left=3mm, right=3mm, top=2mm, bottom=2mm
}

% ── Fill-in helpers ──────────────────────────────────────────────────────────
\newcommand{\blank}[1]{\underline{\hspace{#1}}}
\newcommand{\writeline}{\vspace{1pt}\noindent\textcolor{linegray}{\hrulefill}\vspace{3pt}}

% ── Component table (reusable) ───────────────────────────────────────────────
\newcommand{\componenttable}{%
\renewcommand{\arraystretch}{2.0}
\begin{tabularx}{\linewidth}{@{} >{\bfseries\color{navy}}p{0.22\linewidth} X @{}}
Individual:  & \blank{10.5cm} \\
Population:  & \blank{10.5cm} \\
Sample:      & \blank{10.5cm} \\
Variable(s): & \blank{10.5cm} \\
\end{tabularx}}

% ── List / para settings ─────────────────────────────────────────────────────
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}

%=============================================================================
\begin{document}

% ── Page header ──────────────────────────────────────────────────────────────
\begin{tikzpicture}[remember picture, overlay]
  \fill[navy] (current page.north west)
    rectangle ([yshift=-0.52in]current page.north east);
\end{tikzpicture}
\vspace{-0.42in}
{\color{white}\textbf{\large AP Statistics \hfill Unit 1: Exploring One-Variable Data}}\\[2pt]
{\color{skymid}\small\textbf{Lesson 1.1 \quad Group Activity: Identifying Statistical Components}}
\vspace{0.16in}

\noindent
\begin{tabularx}{\linewidth}{X X X}
Name:\;\blank{4.8cm} & Partner:\;\blank{4.0cm} & Period:\;\blank{1.5cm}
\end{tabularx}

\vspace{0.1in}

% ── Instructions ─────────────────────────────────────────────────────────────
\begin{tcolorbox}[colback=sky, colframe=navy, boxrule=0.8pt, arc=2mm,
    left=3mm, right=3mm, top=2mm, bottom=2mm]
\small
For each headline below, identify the \textbf{individual}, \textbf{population},
\textbf{sample}, and \textbf{variable(s)}. Then answer the follow-up question.
Remember: the \emph{population} is who or what we \emph{want} to know about;
the \emph{sample} is who or what we \emph{actually studied}.
\end{tcolorbox}

\vspace{0.14in}

% ════════════════════════════════════════════════════════════════════════════
% SCENARIO 1
% ════════════════════════════════════════════════════════════════════════════
\begin{scenariobox}[Scenario 1]{navylight}

\begin{headlinebox}{sky}
\small\textit{``A survey of 500 U.S.\ high school students found that 78\% report
feeling stressed about grades at least once a week.''}
\end{headlinebox}

\vspace{8pt}
\componenttable

\vspace{8pt}
\small\textbf{Would it be possible to conduct a census for this study?
Why or why not?}\\[4pt]
\writeline\\[1pt]\writeline

\end{scenariobox}

\vspace{0.16in}

% ════════════════════════════════════════════════════════════════════════════
% SCENARIO 2
% ════════════════════════════════════════════════════════════════════════════
\begin{scenariobox}[Scenario 2]{greenacc}

\begin{headlinebox}{greenbg}
\small\textit{``A national study tracked 1{,}200 elementary school students over
three years and found that those who had at least 30 minutes of recess daily
scored higher on standardized reading assessments.''}
\end{headlinebox}

\vspace{8pt}
\componenttable

\vspace{8pt}
\small\textbf{This study found that more recess is \emph{associated} with higher
reading scores. Does that mean recess \emph{causes} better reading? Explain.}\\[4pt]
\writeline\\[1pt]\writeline

\end{scenariobox}

\vspace{0.16in}

% ════════════════════════════════════════════════════════════════════════════
% SCENARIO 3
% ════════════════════════════════════════════════════════════════════════════
\begin{scenariobox}[Scenario 3 \normalfont\small\color{white!80!black}\quad stretch]{redacc}

\begin{headlinebox}{redbg}
\small\textit{``Scientists examined 60 coral reef sites across the Pacific Ocean
and found that water temperature had increased at 85\% of them over the past decade.''}
\end{headlinebox}

\vspace{8pt}
\componenttable

\vspace{8pt}
\small\textbf{A classmate says: \textit{``The individual is the ocean, because
that's what they're studying.''} Do you agree? Correct any errors in her reasoning.}\\[4pt]
\writeline\\[1pt]\writeline\\[1pt]\writeline

\end{scenariobox}

\vspace{0.16in}

% ── Reflection ───────────────────────────────────────────────────────────────
\begin{tcolorbox}[colback=goldbg, colframe=goldacc, boxrule=0.8pt, arc=2mm,
    left=3mm, right=3mm, top=2mm, bottom=2mm]
\small\textbf{Reflection \textnormal{\color{slate}(answer together, one response per pair):}}
\quad Which scenario was hardest? What made it harder?\\[6pt]
\writeline\\[1pt]\writeline
\end{tcolorbox}

\end{document}
