%! AP Statistics — Unit 3, Lesson 3.1 — Warm-Up
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

\begin{document}

\pageheader{Unit 3, Lesson 3.1}{Warm-Up}
\namedateperiod

\vspace{0.3in}

% ── SECTION 1: Spiral Review ──────────────────────────────────────────────────
{\large\bfseries\color{navy} Part 1 \quad Spiral Review}

\vspace{0.12in}

\begin{enumerate}

    \item From Unit 2 --- identify the \textbf{explanatory} and \textbf{response}
    variable in each scenario, then state whether a \textbf{causal conclusion} is
    possible from an observational study.

    \vspace{8pt}
    \renewcommand{\arraystretch}{1.8}
    \begin{tabularx}{\linewidth}{@{} X p{2.8cm} p{2.8cm} p{2.2cm} @{}}
    \textbf{Scenario} & \textbf{Explanatory} & \textbf{Response} & \textbf{Causal?} \\
    \hline
    Students who sleep more tend to score higher on tests. &
    \blank{2.5cm} & \blank{2.5cm} & \blank{1.8cm} \\
    Eating more vegetables is associated with lower blood pressure. &
    \blank{2.5cm} & \blank{2.5cm} & \blank{1.8cm} \\
    \end{tabularx}

    \vspace{0.18in}

    \item A news site posts an online poll: \textit{``Should the school day start
    later?''} Of 2{,}400 responses, 85\% say yes.
    \begin{enumerate}[label=(\alph*), itemsep=4pt]
        \item Who is likely to respond to an online poll on this topic?\\
        \writeline
        \item Does this result tell us what most students think? Why or why not?\\
        \writeline\writeline
    \end{enumerate}

\end{enumerate}

\vspace{0.35in}

% ── SECTION 2: Looking Ahead ──────────────────────────────────────────────────
{\large\bfseries\color{navy} Part 2 \quad Looking Ahead}

\vspace{0.12in}

\noindent Unit 3 asks: \textit{``Can we trust the data we collected?''}

\vspace{0.14in}

\begin{tcolorbox}[colback=greenbg, colframe=greenacc, boxrule=0.8pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
    \small
    \begin{itemize}[leftmargin=1.3em, itemsep=8pt]
  \item The method used to collect data determines the trustworthiness of the conclusion.
  \item A large sample is \textbf{not} necessarily more trustworthy than a small one.
  \item Chance-based selection is the foundation of trustworthy statistical conclusions.
    \end{itemize}
\end{tcolorbox}

\vspace{0.2in}

\noindent\textcolor{slate}{\small Based on today's big ideas, write one question you have
or one thing you want to understand better:}\\[8pt]
\writeline\\[2pt]\writeline

\end{document}
