%! AP Statistics — Unit 9, Lesson 9.5 — Homework
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

\begin{document}

\pageheader{Unit 9, Lesson 9.5}{Homework}
\namedateperiod

\vspace{0.1in}
\textbf{Directions:} For each problem, carry out a significance test for slope as directed.
Show all work clearly.

\begin{enumerate}

  \item \textbf{Age and Running Speed.} A sports scientist studies the relationship between
        age (years, $x$) and maximum running speed (mph, $y$) in adult recreational runners
        (random sample, $n = 28$).

        \begin{center}
        \renewcommand{\arraystretch}{1.4}
        \begin{tabular}{lrrrr}
            \textbf{Predictor} & \textbf{Coef} & \textbf{SE Coef} & \textbf{T} & \textbf{P} \\
            \hline
            Constant & 12.8 & 1.2   & 10.67 & 0.000 \\
            Age      & $-0.12$ & 0.037 & $-3.24$ & 0.003 \\
        \end{tabular}
        \end{center}

        \begin{enumerate}[label=\alph*.]
          \item State H$_0$ and H$_a$ in terms of $\beta$. Define $\beta$ in context.

                \writelines{3}

          \item Identify the test statistic from the output and verify it by calculation.
                Assume LINER conditions are met.

                $t = \dfrac{b}{SE_b} = \dfrac{\blank{2cm}}{\blank{2cm}} = \blank{2cm}$

                \vspace{0.05in}
                $df = n - 2 = \blank{2cm}$

          \item Interpret the $p$-value in context.
                \writelines{3}

          \item State a conclusion at $\alpha = 0.05$. Does the data provide evidence that
                age is linearly related to maximum running speed?
                \writelines{3}
        \end{enumerate}

  \item \textbf{Absences and Course Grade.} A researcher examines how the number of absences
        ($x$) relates to final course grade ($\%$, $y$) in an introductory statistics course
        (random sample, $n = 35$). Assume LINER conditions are met.

        \begin{center}
        \renewcommand{\arraystretch}{1.4}
        \begin{tabular}{lrrrr}
            \textbf{Predictor} & \textbf{Coef} & \textbf{SE Coef} & \textbf{T} & \textbf{P} \\
            \hline
            Constant  & 91.4 & 2.3  & 39.74 & 0.000 \\
            Absences  & $-2.3$ & 0.54 & $-4.26$ & 0.000 \\
        \end{tabular}
        \end{center}

        \begin{enumerate}[label=\alph*.]
          \item Carry out a complete 4-step significance test at $\alpha = 0.05$.
                \writelines{10}

          \item Construct a 95\% confidence interval for $\beta$ using $t^* = 2.035$
                ($df = 33$). Show your work.
                \writelines{3}

          \item Explain why the confidence interval and the hypothesis test give
                consistent conclusions.
                \writelines{3}
        \end{enumerate}

\end{enumerate}

\end{document}
