%! AP Statistics — Unit 5, Lesson 5.6 — Lesson Plan
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

\begin{document}

\pageheader{Unit 5, Lesson 5.6}{Lesson Plan}

\begin{objectivebox}
\textbf{Topic:} 5.6 — Sampling Distributions for Differences in Sample Proportions\\
\textbf{Enduring Understanding:} UNC-3\\
\textbf{Learning Objectives:} UNC-3.N, UNC-3.O, UNC-3.P\\
\textbf{Essential Knowledge:} UNC-3.N.1; UNC-3.O.1--O.2; UNC-3.P.1--P.3\\
\textbf{Mathematical Practice:} 3.C — Verify conditions; 4.B — Connect representations
\end{objectivebox}

\begin{learningtargetbox}
By the end of this lesson, students will be able to:
\begin{itemize}
  \item State $\mu_{\hat{p}_1 - \hat{p}_2} = p_1 - p_2$ and $\sigma_{\hat{p}_1 - \hat{p}_2} = \sqrt{\frac{p_1(1-p_1)}{n_1} + \frac{p_2(1-p_2)}{n_2}}$.
  \item Check four Large Counts conditions for the normal model.
  \item Compute probabilities for $\hat{p}_1 - \hat{p}_2$ using the normal approximation.
\end{itemize}
\end{learningtargetbox}

\begin{vocabbox}
sampling distribution of $\hat{p}_1 - \hat{p}_2$, four Large Counts conditions, independence between groups
\end{vocabbox}

\begin{hookbox}
\textbf{Hook — Gender Wage Gap (5 min):} A survey finds 68\% of male graduates and 61\% of female graduates are employed full-time within 6 months. Is the 7 percentage-point difference real, or just sampling variability? Lesson 5.6 provides the framework.
\end{hookbox}

\begin{notesbox}
\textbf{Direct Instruction + Guided Practice (30 min):} State formulas for center and spread of $\hat{p}_1 - \hat{p}_2$. Emphasize independence between the two groups (samples drawn separately). Work a full condition-check + probability example. Tiered activity.
\end{notesbox}

\begin{reflectionbox}
\textbf{Exit Ticket + Homework:} Two-proportion sampling distribution problems.\\
\textbf{AP Connection:} UNC-3.N--P directly tested; these formulas are on the AP formula sheet.
\end{reflectionbox}

\end{document}
