%! AP Statistics — Unit 1, Lesson 1.3 — Homework
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

%=============================================================================
\begin{document}

\pageheader{Unit 1, Lesson 1.3}{Homework: Representing a Categorical Variable with Tables}
\namedateperiod

\vspace{0.1in}

\begin{tcolorbox}[colback=sky, colframe=navy, boxrule=0.8pt, arc=2mm,
    left=3mm, right=3mm, top=1.5mm, bottom=1.5mm]
\small For all problems: show your calculations, include context in written responses,
and verify that your relative frequencies sum to 1. AP free-response requires complete
sentences --- practice that habit here.
\end{tcolorbox}

\vspace{0.14in}

% ════════════════════════════════════════════════════════════════════════════
% PART A
% ════════════════════════════════════════════════════════════════════════════
\begin{blurbbox}[Part A \quad Build a Frequency Table from Raw Data]{navylight}
\small

A survey asked 25 students to name their preferred type of music.
The responses are listed below.

\vspace{8pt}
\begin{center}
\begin{tabular}{*{5}{p{1.6cm}}}
Pop  & Hip-Hop & Rock   & Pop     & Classical \\
Rock & Pop     & Hip-Hop& Rock    & Pop \\
Hip-Hop & Pop  & Classical & Hip-Hop & Rock \\
Pop  & Rock    & Pop    & Hip-Hop & Classical \\
Hip-Hop & Rock & Pop    & Classical & Hip-Hop \\
\end{tabular}
\end{center}

\vspace{12pt}

\renewcommand{\arraystretch}{2.0}
\begin{tabularx}{\linewidth}{@{} >{\bfseries}p{0.22\linewidth}
                                    C{0.16\linewidth}
                                    C{0.2\linewidth}
                                    C{0.22\linewidth} @{}}
\rowcolor{sky}
\textbf{Music type} & \textbf{Tally} & \textbf{Frequency} & \textbf{Rel.\ Frequency} \\
\midrule
Classical  & & & \\
Hip-Hop    & & & \\
Pop        & & & \\
Rock       & & & \\
\midrule
\rowcolor{sky}\textbf{Total} & & \blank{2cm} & \blank{2.5cm} \\
\end{tabularx}

\vspace{12pt}

\begin{enumerate}[leftmargin=1.5em, itemsep=8pt]
  \item Write 2--3 complete sentences describing the distribution of preferred music
        type for these 25 students. Include the most common and least common categories
        and their relative frequencies.\\[8pt]
        \writeline\\[1pt]\writeline\\[1pt]\writeline

  \item What percent of students prefer rock or pop? Show your work.\\[8pt]
        \writeline\\[1pt]\writeline
\end{enumerate}

\end{blurbbox}

\vspace{0.14in}

% ════════════════════════════════════════════════════════════════════════════
% PART B
% ════════════════════════════════════════════════════════════════════════════
\begin{blurbbox}[Part B \quad Compare Two Groups Using Relative Frequency]{greenacc}
\small

Two different classes were surveyed about their favorite season.
The counts are shown below.

\vspace{8pt}
\renewcommand{\arraystretch}{1.6}
\begin{tabularx}{\linewidth}{@{} >{\bfseries}p{0.18\linewidth}
                                    C{0.14\linewidth} C{0.2\linewidth}
                                    C{0.14\linewidth} C{0.2\linewidth} @{}}
\rowcolor{sky}
\textbf{Season} & \textbf{Class A} & \textbf{Rel.\ Freq.\ A}
                & \textbf{Class B} & \textbf{Rel.\ Freq.\ B} \\
\midrule
Spring & 6  & \blank{2cm} & 12 & \blank{2cm} \\
Summer & 14 & \blank{2cm} & 16 & \blank{2cm} \\
Fall   & 5  & \blank{2cm} & 10 & \blank{2cm} \\
Winter & 5  & \blank{2cm} & 2  & \blank{2cm} \\
\midrule
\rowcolor{sky}\textbf{Total} & 30 & \blank{2cm} & 40 & \blank{2cm} \\
\end{tabularx}

\vspace{10pt}

\begin{enumerate}[leftmargin=1.5em, itemsep=8pt]
  \item Which season is the most popular in Class A? In Class B?
        Use relative frequencies to support your answer.\\[6pt]
        \writeline\\[1pt]\writeline

  \item A student claims that summer is more popular in Class B because
        Class B has 16 students who prefer it vs.\ 14 in Class A.
        Is this reasoning correct? Why or why not?\\[6pt]
        \writeline\\[1pt]\writeline

  \item Which class shows a stronger preference for winter? Support your
        answer with relative frequencies.\\[6pt]
        \writeline\\[1pt]\writeline
\end{enumerate}

\end{blurbbox}

\vspace{0.14in}

% ════════════════════════════════════════════════════════════════════════════
% PART C
% ════════════════════════════════════════════════════════════════════════════
\begin{blurbbox}[Part C \quad AP-Style Free Response]{redacc}
\small

The table below shows the distribution of dominant hand for a sample of
120 college athletes.

\vspace{8pt}
\renewcommand{\arraystretch}{1.6}
\begin{tabularx}{0.7\linewidth}{@{} >{\bfseries}p{0.32\linewidth}
                                      C{0.22\linewidth}
                                      C{0.26\linewidth} @{}}
\rowcolor{sky}
\textbf{Dominant hand} & \textbf{Frequency} & \textbf{Rel.\ Frequency} \\
\midrule
Right    & 96  & 0.800 \\
Left     & 18  & 0.150 \\
Ambidextrous & 6 & 0.050 \\
\midrule
\rowcolor{sky}\textbf{Total} & 120 & 1.000 \\
\end{tabularx}

\vspace{10pt}

\begin{enumerate}[leftmargin=1.5em, itemsep=10pt]
  \item Describe the distribution of dominant hand for these athletes using
        the information in the table.\\[6pt]
        \writeline\\[1pt]\writeline\\[1pt]\writeline

  \item A classmate says: ``Most athletes are right-handed, so there's nothing
        interesting here.'' What additional comparison might make this table
        more informative?\\[6pt]
        \writeline\\[1pt]\writeline
\end{enumerate}

\end{blurbbox}

\vspace{0.14in}

% ════════════════════════════════════════════════════════════════════════════
% EXTENSION
% ════════════════════════════════════════════════════════════════════════════
\begin{extensionbox}
\small
\textbf{Optional Extension --- Find a Real Frequency Table}\\[4pt]
Find a published frequency or relative frequency table from a real source
(e.g., \texttt{data.census.gov}, \texttt{pewresearch.org}, a news article).
Write a 3--5 sentence description of the distribution it shows. Include:
(1) the source and total sample size, (2) the most and least common categories,
(3) one comparison or observation that is \textit{not} obvious from a quick glance.

\vspace{8pt}
\writeline\\[1pt]\writeline\\[1pt]\writeline\\[1pt]\writeline\\[1pt]\writeline

\vspace{4pt}
\textcolor{slate}{\scriptsize Source / URL:\;\blank{11cm}}
\end{extensionbox}

\end{document}
