%! AP Statistics — Unit 2, Lesson 2.3 — Homework
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

%=============================================================================
\begin{document}

\pageheader{Unit 2, Lesson 2.3}{Homework}
\namedateperiod

\vspace{0.2in}

% ── PROBLEM 1 ─────────────────────────────────────────────────────────────────
\begin{tcolorbox}[colback=sky, colframe=navy, boxrule=0.9pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small\textbf{Problem 1 --- Helmet Use and Injuries}\\[4pt]
A study of 500 recreational cyclists recorded helmet use (Yes / No) and whether the
cyclist sustained a head injury during the season (Yes / No).

\vspace{8pt}
\renewcommand{\arraystretch}{1.8}
\begin{tabularx}{\linewidth}{@{} l C{3cm} C{3cm} C{2.4cm} @{}}
\rowcolor{sky}
                          & \textbf{Injury: Yes} & \textbf{Injury: No} & \textbf{Row Total} \\
\hline
\textbf{Helmet: Yes}      & 15 & 285 & \blank{1.8cm} \\
\textbf{Helmet: No}       & 40 & 160 & \blank{1.8cm} \\
\hline
\textbf{Col.\ Total}      & \blank{1.8cm} & \blank{1.8cm} & \blank{1.8cm} \\
\end{tabularx}
\end{tcolorbox}

\vspace{0.14in}

\begin{enumerate}[leftmargin=1.6em, itemsep=0.16in]

    \item Fill in all missing totals. Then compute the conditional proportion of cyclists
          with a head injury for each helmet group. Show your work.\\[10pt]
          $\hat{p}_{\text{helmet}} = \blank{2.4cm}$ \hfill $\hat{p}_{\text{no helmet}} = \blank{2.4cm}$

    \item Compute the difference in proportions (helmet $-$ no helmet) and interpret in context.\\[10pt]
          Difference: \blank{3cm}\\[8pt]
          \writeline\\[2pt]\writeline

    \item Compute the relative risk of injury for helmet wearers compared to non-wearers and
          interpret in context.\\[10pt]
          RR: \blank{3cm}\\[8pt]
          \writeline\\[2pt]\writeline

    \item A news headline reads: \textit{``Cyclists without helmets are injured at twice the
          rate of helmet wearers.''} Is this claim accurate based on your calculation?
          Explain using your relative risk value.\\[8pt]
          \writeline\\[2pt]\writeline\\[2pt]\writeline

\end{enumerate}

\vspace{0.22in}

% ── PROBLEM 2 ─────────────────────────────────────────────────────────────────
\begin{tcolorbox}[colback=sky, colframe=navy, boxrule=0.9pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small\textbf{Problem 2 --- Screen Time and Sleep Quality}\\[4pt]
In a survey of 240 teenagers, participants were classified by daily screen time before bed
(High: $>$ 2 hrs / Low: $\leq$ 2 hrs) and self-reported sleep quality (Good / Poor).
Among 90 high-screen-time teens, 63 reported poor sleep.
Among 150 low-screen-time teens, 45 reported poor sleep.
\end{tcolorbox}

\vspace{0.14in}

\begin{enumerate}[leftmargin=1.6em, itemsep=0.16in]

    \item Construct a completed two-way table for this data.

    \vspace{0.1in}
    \renewcommand{\arraystretch}{1.8}
    \begin{tabularx}{\linewidth}{@{} l C{2.8cm} C{2.8cm} C{2.4cm} @{}}
    \rowcolor{sky}
                              & \textbf{Sleep: Poor} & \textbf{Sleep: Good} & \textbf{Row Total} \\
    \hline
    \textbf{Screen: High}     & \blank{1.8cm} & \blank{1.8cm} & \blank{1.8cm} \\
    \textbf{Screen: Low}      & \blank{1.8cm} & \blank{1.8cm} & \blank{1.8cm} \\
    \hline
    \textbf{Col.\ Total}      & \blank{1.8cm} & \blank{1.8cm} & \blank{1.8cm} \\
    \end{tabularx}

    \item Compute the difference in proportions and relative risk for poor sleep
          (High screen $-$ Low screen). Show all work.\\[10pt]
          $\hat{p}_{\text{high}} = \blank{2.4cm}$ \quad $\hat{p}_{\text{low}} = \blank{2.4cm}$\\[10pt]
          Difference: \blank{3cm} \hfill RR: \blank{3cm}

    \item Write a two-sentence conclusion about the association between screen time and
          sleep quality, incorporating both statistics.\\[8pt]
          \writeline\\[2pt]\writeline\\[2pt]\writeline\\[2pt]\writeline

    \item \textbf{Reflection:} For which problem --- helmet use or screen time --- is the
          relative risk more useful to emphasize? Why?\\[8pt]
          \writeline\\[2pt]\writeline\\[2pt]\writeline

\end{enumerate}

\vspace{0.14in}

% ── AP-STYLE FRQ PREVIEW ──────────────────────────────────────────────────────
\begin{tcolorbox}[colback=goldbox, colframe=navy, boxrule=0.8pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small\textbf{AP Connection}\\[4pt]
On the AP Exam, you may be asked to ``calculate and interpret'' a statistic. That means two
things: (1) show the correct computation with numbers, and (2) write a sentence placing the
number in the context of the problem (naming the variables and groups). Practice writing full
interpretations on every problem above.
\end{tcolorbox}

\end{document}
