%! AP Statistics — Unit 9, Lesson 9.4 — Homework
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

\begin{document}

\pageheader{Unit 9, Lesson 9.4}{Homework}
\namedateperiod

\vspace{0.1in}

\textbf{Problem 1.} A random sample of 28 college students was surveyed. The
explanatory variable is hours per week spent on social media ($x$) and the response
variable is GPA ($y$). A residual plot shows random scatter with no curve and constant
spread. The residuals appear approximately normal.

\begin{enumerate}[label=\alph*.]

  \item Name the appropriate inference procedure.

        \writelines{1}

  \item Define $\beta$ in context and state H$_0$ and H$_a$.

        $\beta = $ \writeline

        H$_0$: \blank{8cm} \quad H$_a$: \blank{8cm}

  \item Verify each LINER condition using the information given. For each, state
        whether it is met and explain.

        \writelines{5}

  \item One condition cannot be fully verified from the information given. Which
        one, and what additional information would you need?

        \writelines{2}

\end{enumerate}

\vspace{0.1in}

\textbf{Problem 2.} For each scenario below, state the appropriate H$_0$ and H$_a$
in terms of $\beta$, and explain what $\beta = 0$ means in context.

\begin{enumerate}[label=\alph*.]

  \item $x = $ daily rainfall (inches), $y = $ umbrella sales, $n = 60$ days
        (random sample).

        H$_0$: \blank{7cm} \quad H$_a$: \blank{7cm}

        $\beta = 0$ means: \writelines{1}

  \item $x = $ age (years), $y = $ marathon finish time (minutes), $n = 45$ runners
        (random sample). The researcher suspects older runners take longer, so she
        considers a one-sided test.

        H$_0$: \blank{7cm} \quad H$_a$: \blank{7cm}

        $\beta = 0$ means: \writelines{1}

  \item $x = $ class size, $y = $ average exam score, $n = 35$ classes (random sample).
        A teacher claims larger classes score lower ($\beta < -1$). State hypotheses
        to test this claim.

        H$_0$: \blank{7cm} \quad H$_a$: \blank{7cm}

        $\beta = 0$ means: \writelines{1}

\end{enumerate}

\end{document}
