%! AP Statistics — Unit 1, Lesson 1.2 — Exit Ticket
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

%=============================================================================
\begin{document}

\pageheader{Unit 1, Lesson 1.2}{Exit Ticket}
\namedateperiod

\vspace{0.22in}

\begin{tcolorbox}[colback=sky, colframe=navy, boxrule=0.9pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small A researcher is studying music listening habits. For each variable below,
identify the type: \textbf{Categorical (C)}, \textbf{Quantitative Discrete (QD)},
or \textbf{Quantitative Continuous (QC)}. Write a one-phrase justification.
\end{tcolorbox}

\vspace{0.2in}

\renewcommand{\arraystretch}{2.6}
\begin{tabularx}{\linewidth}{@{} c >{\raggedright\arraybackslash}p{0.38\linewidth}
                                    C{0.12\linewidth} X @{}}
\rowcolor{sky}
\textbf{\#} & \textbf{Variable} & \textbf{Type} & \textbf{Justification} \\
\midrule
1 & Favorite music genre (pop, rock, jazz, \ldots)
  & \blank{1.5cm} & \blank{6cm} \\
2 & Number of songs on a playlist
  & \blank{1.5cm} & \blank{6cm} \\
3 & Duration of the longest song on the playlist (minutes)
  & \blank{1.5cm} & \blank{6cm} \\
4 & Country of birth of the artist
  & \blank{1.5cm} & \blank{6cm} \\
5 & Temperature at an outdoor concert venue at noon (°F)
  & \blank{1.5cm} & \blank{6cm} \\
\end{tabularx}

\vspace{0.24in}

% ── AP-STYLE MC ──────────────────────────────────────────────────────────────
\begin{tcolorbox}[colback=redbg, colframe=redacc, boxrule=0.8pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small\textbf{AP-Style Practice}\\[6pt]
A survey records each respondent's \textit{annual income} (in dollars) and
\textit{job type} (teacher, engineer, nurse, other).
Which of the following correctly classifies both variables?

\vspace{10pt}
\begin{enumerate}[label=\textbf{(\Alph*)}, leftmargin=2em, itemsep=6pt]
  \item Annual income is categorical; job type is quantitative.
  \item Annual income is quantitative discrete; job type is categorical.
  \item Annual income is quantitative continuous; job type is categorical.
  \item Both variables are categorical because they describe characteristics of a person.
\end{enumerate}
\end{tcolorbox}

\vspace{0.12in}
\noindent\textcolor{slate}{\small My answer: \blank{1cm} \quad Because: \blank{8.5cm}}

\end{document}
