%! AP Statistics — Unit 4, Lesson 4.9 — Student Packet Cover Sheet
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}
\usepackage{ltablex}
\keepXColumns

\begin{document}

% Full-bleed navy banner
\begin{tikzpicture}[remember picture, overlay]
  \fill[navy] (current page.north west)
    rectangle ([yshift=-0.9in]current page.north east);
\end{tikzpicture}
\vspace{-0.8in}

\begin{center}
  {\color{white}\textbf{\LARGE AP Statistics}}\\[4pt]
  {\color{skymid}\large\textbf{Unit 4: Probability, Random Variables, and Probability Distributions}}\\[6pt]
  {\color{white}\textbf{\large Lesson 4.9 \quad Combining Random Variables}}
\end{center}

\vspace{0.22in}
\namedateperiod
\vspace{0.18in}

\begin{learningtargetbox}
\small
\begin{enumerate}[leftmargin=1.5em, itemsep=5pt]
  \item \ldots{} find the mean and standard deviation of a linear transformation
        $W = a + bX$ using $\mu_W = a + b\mu_X$ and $\sigma_W = |b|\sigma_X$.
  \item \ldots{} find the mean and variance of the sum or difference of two independent
        random variables using $\mu_{X \pm Y} = \mu_X \pm \mu_Y$ and
        $\sigma^2_{X \pm Y} = \sigma^2_X + \sigma^2_Y$.
  \item \ldots{} explain why variances add for independent random variables but
        standard deviations do not.
\end{enumerate}
\end{learningtargetbox}

\vspace{0.14in}

\begin{tocbox}
\small
\renewcommand{\arraystretch}{1.5}
\begin{tabularx}{\linewidth}{@{} c l X r @{}}
\rowcolor{sky}
\textbf{\#} & \textbf{Component} & \textbf{Description} & \textbf{Score} \\
\midrule
1 & Warm-Up        & Spiral review: $\mu_X$ and $\sigma_X$ from Lesson 4.8 & \blank{1.2cm} \\
2 & Guided Notes   & Transformation, sum, and difference rules              & \blank{1.2cm} \\
3 & Group Activity & Applying combining rules in context (3 tiers)          & \blank{1.2cm} \\
4 & Exit Ticket    & Sum and difference: food-truck context                 & \blank{1.2cm} \\
5 & Homework       & Linear transformations; sums and differences           & \blank{1.2cm} \\
\midrule
  & \multicolumn{2}{r}{\textbf{Total}} & \blank{1.2cm} \\
\end{tabularx}
\end{tocbox}

\vspace{0.14in}

\begin{remindbox}
\small
The \textbf{most important idea in Lesson 4.9}: variances add; standard deviations do not.

\vspace{6pt}
\begin{tabularx}{\linewidth}{@{} >{\centering\arraybackslash\columncolor{goldbg}}p{0.06\linewidth}
                                    X @{}}
\textbf{\large!} &
\textbf{Always add variances first.}\enspace
To find the SD of a sum or difference, compute $\sigma^2_{X+Y} = \sigma^2_X + \sigma^2_Y$
first, then take the square root. Never add standard deviations directly. \\[6pt]
\textbf{\large!} &
\textbf{Subtraction increases spread.}\enspace
$\sigma^2_{X-Y} = \sigma^2_X + \sigma^2_Y$ --- the variance of a difference is
\emph{larger} than either component's variance, not smaller. \\[6pt]
\textbf{\large!} &
\textbf{Independence is required.}\enspace
The variance addition rule only applies to independent random variables. Always
check for independence before using these formulas. \\
\end{tabularx}
\end{remindbox}

\end{document}
