%! AP Statistics — Unit 1, Lesson 1.6 — Warm-Up ANSWER KEY
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-key}

%=============================================================================
\begin{document}

\pageheader{Unit 1, Lesson 1.6}{Warm-Up --- Answer Key}
\begin{tabularx}{\linewidth}{X X X}
Name:\;\ans{Key} & Date:\; & Period:\;
\end{tabularx}

\vspace{0.18in}

\noindent Homework hours per week for 30 students (histogram via bar lengths):

\vspace{0.1in}

\begin{center}
\small
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{@{} >{\bfseries}p{0.22\linewidth} p{0.70\linewidth} @{}}
\rowcolor{sky}
\textbf{Hours / Week} & \textbf{Frequency} \\
\midrule
0--under 4   & 3 \\
4--under 8   & 9 \\
8--under 12  & 11 \\
12--under 16 & 6 \\
16--under 20 & 1 \\
\end{tabular}
\end{center}

\vspace{0.18in}

\begin{enumerate}

  \item \ans{Roughly symmetric (or slightly skewed right). The tallest bar is
        in the 8--12 interval, with bars falling off on both sides. The slight
        skew right comes from the longer right tail (fewer students with very
        high homework hours). Accept ``unimodal'' as a secondary descriptor.}

  \begin{teachernote}
  The goal is to activate shape vocabulary before formal instruction. Accept
  ``skewed right'' if students note the longer right tail. The key is that they
  support their answer with a feature of the display.
  \end{teachernote}

  \item \ans{Approximately 8--10 hours per week. The tallest bar (most students)
        falls in the 8--12 interval, so the typical value is somewhere in that
        range. A reasonable estimate is 9--10 hours. Accept any value in the
        8--12 range with a reasonable justification.}

  \item \ans{The student who works 16--20 hours (only 1 student) could be
        considered a potential outlier --- this interval is far from the main
        cluster of 4--16 hours. The 0--4 interval (3 students) is less extreme
        but worth noting. No formal rule yet; visual inspection is appropriate.}

\end{enumerate}

\vspace{0.14in}

\begin{tcolorbox}[colback=greenbg, colframe=greenacc, boxrule=0.8pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small
\begin{itemize}[leftmargin=1.3em, itemsep=5pt]
  \item Today we formalize SOCS: \textbf{S}hape, \textbf{O}utliers,
        \textbf{C}enter, and \textbf{S}pread.
  \item Students already have intuitions about these four components ---
        SOCS gives them a complete, AP-scorable structure.
  \item Context in every sentence is the most commonly missed AP requirement.
\end{itemize}
\end{tcolorbox}

\end{document}
