%! AP Statistics — Unit 7, Lesson 7.1 — Warm-Up (Answer Key)
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-key}
\newcommand{\TallMath}[1]{$\displaystyle #1\rule[-1.4em]{0pt}{3.2em}$}

\begin{document}

\pageheader{Unit 7, Lesson 7.1}{Warm-Up --- Answer Key}
\namedateperiod

\vspace{0.15in}

A researcher conducts a study to determine whether the mean daily screen time for
teenagers differs from 7 hours. She takes a random sample of 40 teenagers and finds
$\bar x = 7.6$ hours with $s = 1.4$ hours.

\begin{enumerate}
  \item From Unit 5, describe the sampling distribution of $\bar x$ (assuming the
        population is approximately normal). Include shape, center, and standard deviation.

        \begin{itemize}
          \item \textbf{Shape:} \ans{Approximately normal (CLT applies, $n = 40 \ge 30$)}
          \item \textbf{Center:} $\mu_{\bar x} = $ \ans{$\mu = 7$ hours (under $H_0$)}
          \item \textbf{Spread:} $\sigma_{\bar x} = \sigma/\sqrt{n} \approx s/\sqrt{n} = $
                \ans{$1.4/\sqrt{40} \approx 0.221$ hours}
        \end{itemize}

        \vspace{0.05in}

  \item The researcher tests $H_0{:}\ \mu = 7$ vs.\ $H_a{:}\ \mu \ne 7$ at $\alpha = 0.05$.
        She rejects $H_0$.

        \begin{enumerate}[label=\alph*.]
          \item If the true mean daily screen time is actually 7 hours, what type of
                error did the researcher commit? \quad
                \textcolor{keyred}{\textbf{Type I}} \quad (Type II) \quad (No error)

                \vspace{0.05in}
          \item What is the probability that the researcher commits this type of error,
                assuming the test was conducted correctly?
                \ans{$\alpha = 0.05$ (5\%)}
        \end{enumerate}

        \vspace{0.05in}

  \item Suppose instead the researcher \emph{fails to reject} $H_0$, but the true
        mean screen time is actually 8 hours.

        \begin{enumerate}[label=\alph*.]
          \item What type of error has the researcher committed? \quad
                (Type I) \quad \textcolor{keyred}{\textbf{Type II}} \quad (No error)

                \vspace{0.05in}
          \item In Unit 7 we will study procedures for \emph{means} using the
                $t$-distribution. Write one question you have about how errors in
                inference for means differ from errors in inference for proportions.

                \begin{teachernote}
                    Accept any reasonable question. The Type I error rate is still
                    controlled by $\alpha$ regardless of whether we use $z$ or $t$.
                    Substituting $s$ for $\sigma$ does not change the Type I error rate;
                    it changes the critical value from $z^*$ to $t^*$.
                \end{teachernote}
        \end{enumerate}
\end{enumerate}

\end{document}
