%! Skills Focus: Selecting Inference Procedures — Unit 7, Lesson 7.10 — Warm-Up (Answer Key)
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-key}   % pulls in -boxes; do NOT also load -boxes
\newcommand{\TallMath}[1]{$\displaystyle #1\rule[-1.4em]{0pt}{3.2em}$}

\begin{document}

\pageheader{Unit 7, Lesson 7.10}{Warm-Up --- Answer Key}
\namedateperiod

\vspace{0.12in}

\begin{notesbox}{Spiral Review --- Identifying Inference Procedures (Units 6--7)}

\textit{For each scenario, identify the correct inference procedure. No computation needed.}

\vspace{0.06in}
\textbf{1.} A polling firm surveys 400 randomly selected registered voters and asks whether
they support a proposed tax increase. The firm wants to estimate the true proportion of all
registered voters who support the measure.

\begin{enumerate}[label=\alph*.]
  \item Is the parameter a proportion or a mean? \ans{proportion}
  \item How many samples? \ans{one}
  \item Estimate or test? \ans{estimate (CI)}
  \item Name the procedure: \ans{one-sample $z$-interval for $p$}
\end{enumerate}

\vspace{0.10in}
\textbf{2.} A researcher records the resting pulse rates of 18 randomly selected adults before
and after a 6-week yoga program (same subjects, measured twice). She wants to know whether the
program \emph{reduced} mean resting pulse rate.

\begin{enumerate}[label=\alph*.]
  \item Is the parameter a proportion or a mean? \ans{mean}
  \item Is this one sample, matched pairs, or two independent samples? \ans{matched pairs}
  \item Name the procedure: \ans{matched-pairs $t$-test for $\mu_d$}
\end{enumerate}

\vspace{0.10in}
\textbf{3.} A university administrator randomly selects 50 students from the engineering program
and 50 from the humanities program and records whether each student holds a part-time job. She
wants to test whether the proportions who hold part-time jobs differ between programs.

Name the procedure: \ans{two-sample $z$-test for $p_1 - p_2$}

\vspace{0.10in}
\textbf{4.} A nutritionist randomly samples 35 adults and records their daily calcium intake
(in mg). She wants to test whether the mean intake is below the recommended 1,000 mg.

Name the procedure: \ans{one-sample $t$-test for $\mu$}

\end{notesbox}

\end{document}
