%! AP Statistics — Unit 9, Lesson 9.3 — Group Activity (Answer Key)
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-key}

\begin{document}

\pageheader{Unit 9, Lesson 9.3}{Group Activity --- Answer Key}
\namepartnerperiod

\vspace{0.1in}
Three research teams each fit a regression model and reported a 95\% confidence interval
for the slope. The intervals are already computed --- your job is to interpret them and
evaluate researcher claims.

\vspace{0.08in}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{clllcc}
    \textbf{Study} & \textbf{Explanatory ($x$)} & \textbf{Response ($y$)} &
    \textbf{Population} & \textbf{95\% CI} & \textbf{$n$} \\
    \hline
    A & Daily screen time (hr) & Sleep duration (hr) & High school students & $(-0.31,\ -0.05)$ & 45 \\
    B & Advertising spend (\$1000s) & Monthly sales (\$1000s) & Small retailers & $(-0.8,\ 2.1)$ & 28 \\
    C & Elevation (100 ft) & Avg.\ July temperature ($^\circ$F) & Weather stations & $(-3.2,\ -0.9)$ & 20 \\
\end{tabular}
\end{center}

\vspace{0.1in}

\begin{tcolorbox}[colback=white, colframe=black!40,
    title=\textbf{Tier R --- Remediate (Key)},
    fonttitle=\bfseries, arc=2mm, left=3mm, right=3mm, top=2mm, bottom=2mm]

\textbf{1.} Sentence frame:

\ans{We are 95\% confident that the true slope relating sleep duration to daily screen time
for high school students is between $-0.31$ and $-0.05$ hours of sleep per hour of screen time.}

\vspace{0.1in}
\textbf{2.} Is 0 in the interval $(-0.31,\ -0.05)$? \quad \textcolor{keyred}{\textbf{No}}

Therefore, there \ans{is} evidence that $\beta \ne 0$.

\vspace{0.1in}
\textbf{3.} Is $-0.1$ in the interval $(-0.31,\ -0.05)$? \quad \textcolor{keyred}{\textbf{Yes}}

Is the claim $\beta = -0.1$ consistent with the data?
\ans{Yes --- $-0.1$ is inside the interval, so this claim is consistent with the data.}

\end{tcolorbox}

\begin{tcolorbox}[colback=white, colframe=black!40,
    title=\textbf{Tier A --- Approaching Proficiency (Key)},
    fonttitle=\bfseries, arc=2mm, left=3mm, right=3mm, top=2mm, bottom=2mm]

\begin{enumerate}[label=\alph*.]

  \item Interpretations:

        Study A: \ans{We are 95\% confident that the true slope of the population regression line
        relating sleep duration to daily screen time for high school students is between $-0.31$
        and $-0.05$ hours of sleep per hour of screen time.}

        Study B: \ans{We are 95\% confident that the true slope of the population regression line
        relating monthly sales to advertising spend for small retailers is between $-0.8$ and
        $2.1$ thousand dollars of sales per thousand dollars of advertising.}

        Study C: \ans{We are 95\% confident that the true slope of the population regression line
        relating average July temperature to elevation for weather stations is between $-3.2$
        and $-0.9$ degrees Fahrenheit per 100 feet of elevation.}

  \item Evidence that $\beta \ne 0$?

        Study A: \ans{Yes. Since 0 is not in $(-0.31,\ -0.05)$, this provides evidence that
        $\beta \ne 0$; there is a negative linear relationship between screen time and sleep.}

        Study B: \ans{No. Since 0 is contained in $(-0.8,\ 2.1)$, the interval is consistent
        with $\beta = 0$; we cannot conclude a linear relationship exists.}

        Study C: \ans{Yes. Since 0 is not in $(-3.2,\ -0.9)$, this provides evidence that
        $\beta \ne 0$; there is a negative linear relationship between elevation and temperature.}

  \item Researcher claims:

        Study A ($\beta = 0$): \ans{0 is not in $(-0.31,\ -0.05)$, so this provides evidence
        against $\beta = 0$.}

        Study B ($\beta = 1.5$): \ans{1.5 is in $(-0.8,\ 2.1)$, so $\beta = 1.5$ is consistent
        with the data.}

        Study C ($\beta = -2.0$): \ans{$-2.0$ is in $(-3.2,\ -0.9)$, so $\beta = -2.0$ is
        consistent with the data.}

\end{enumerate}
\end{tcolorbox}

\begin{tcolorbox}[colback=white, colframe=black!40,
    title=\textbf{Tier E --- Extension (Key)},
    fonttitle=\bfseries, arc=2mm, left=3mm, right=3mm, top=2mm, bottom=2mm]

\textbf{Bonus 1.}
\ans{Because 0 is contained in the interval $(-0.8,\ 2.1)$, the data are consistent with
$\beta = 0$ (no linear relationship), so the interval does not provide evidence that
advertising spend is linearly related to monthly sales.}

\vspace{0.1in}
\textbf{Bonus 2.}
\ans{With $n = 80$ instead of $n = 20$, the standard error $SE_b$ would decrease, producing
a narrower CI. The new interval would be narrower than $(-3.2,\ -0.9)$. Since $-2.0$ falls
inside the original interval and the new interval would be centered at roughly the same value
of $b$, it is likely (though not guaranteed) that $-2.0$ would still be contained in the
narrower interval.}

\end{tcolorbox}

\end{document}
