%! AP Statistics — Unit 3, Lesson 3.6 — Homework KEY
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-key}

\begin{document}

\pageheader{Unit 3, Lesson 3.6}{Homework — KEY}
\namedateperiod

\vspace{0.1in}

\begin{practicebox}
\small
\textbf{1.}
\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=5pt]
  \item \ans{Block design (blocking by gender)}
  \item \ans{Gender is a known variable that may affect anxiety response to mindfulness training. Blocking removes this variability, giving a more precise estimate of the treatment effect. With 20 men and 20 women, random assignment within blocks is straightforward.}
  \item \begin{teachernote}Diagram: 40 students $\to$ Block 1 (men, 20) / Block 2 (women, 20); within each block, randomly assign 10 to mindfulness, 10 to control.\end{teachernote}
\end{enumerate}

\vspace{6pt}
\textbf{2.}
\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=5pt]
  \item \ans{Matched pairs design}
  \item \ans{Each patient controls for their own individual factors (diet, saliva chemistry, brushing habits). By applying both brands to the same patient (one side each), all individual differences are controlled, giving maximum precision.}
\end{enumerate}

\vspace{6pt}
\textbf{3.}
\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=5pt]
  \item \ans{CRD (completely randomized design)}
  \item \ans{All seedlings are from the same variety grown under the same conditions — they are homogeneous. There is no known nuisance variable to block on, so a CRD is the simplest and most appropriate design.}
\end{enumerate}

\vspace{6pt}
\textbf{4.} \ans{A CRD is preferable when the blocking variable is not measurable before the study begins, when the variable's effect on the response is very small (blocking would gain little precision), or when the added logistical complexity of blocking outweighs the benefit. For example, if the nuisance variable is only weakly related to the response, blocking may not meaningfully reduce variability.}
\end{practicebox}

\end{document}
