%! AP Statistics — Unit 3, Lesson 3.1 — Warm-Up KEY
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-key}

\begin{document}

\pageheader{Unit 3, Lesson 3.1}{Warm-Up --- Answer Key}
\begin{tabularx}{\linewidth}{X X X}
Name:\;\ans{Key} & Date:\; & Period:\;
\end{tabularx}

\vspace{0.3in}

{\large\bfseries\color{navy} Part 1 \quad Spiral Review}

\vspace{0.12in}

\begin{enumerate}

    \item
    \renewcommand{\arraystretch}{1.8}
    \begin{tabularx}{\linewidth}{@{} X p{2.8cm} p{2.8cm} p{2.2cm} @{}}
    \textbf{Scenario} & \textbf{Explanatory} & \textbf{Response} & \textbf{Causal?} \\
    \hline
    Students who sleep more tend to score higher on tests. &
    \ans{Sleep} & \ans{Test score} & \ans{No} \\
    Eating more vegetables is associated with lower blood pressure. &
    \ans{Vegetables} & \ans{Blood pressure} & \ans{No} \\
    \end{tabularx}

    \vspace{0.18in}

    \item
    \begin{enumerate}[label=(\alph*), itemsep=4pt]
        \item \ans{People who feel strongly about the issue (likely students who want a
        later start time) are more likely to click and vote.}
        \item \ans{No --- only people who visit the site and feel strongly enough to
        respond are represented. Many students who don't have strong opinions are not
        counted. This is voluntary response bias.}
    \end{enumerate}

\end{enumerate}

\vspace{0.35in}

{\large\bfseries\color{navy} Part 2 \quad Looking Ahead}

\vspace{0.12in}

\noindent Unit 3 asks: \textit{``Can we trust the data we collected?''}

\vspace{0.14in}

\begin{tcolorbox}[colback=greenbg, colframe=greenacc, boxrule=0.8pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
    \small
    \begin{itemize}[leftmargin=1.3em, itemsep=8pt]
  \item The method used to collect data determines the trustworthiness of the conclusion.
  \item A large sample is \textbf{not} necessarily more trustworthy than a small one.
  \item Chance-based selection is the foundation of trustworthy statistical conclusions.
    \end{itemize}
\end{tcolorbox}

\vspace{0.2in}

\noindent\textcolor{slate}{\small Student responses will vary.}

\end{document}
