%! AP Statistics — Unit 2, Lesson 2.3 — Group Activity
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

%=============================================================================
\begin{document}

\pageheader{Unit 2, Lesson 2.3}{Group Activity}
\namepartnerperiod

\vspace{0.18in}

% ── SCENARIO ─────────────────────────────────────────────────────────────────
\begin{tcolorbox}[colback=sky, colframe=navy, boxrule=0.9pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small\textbf{Context:} A public-health agency studied sleep habits and academic performance.
A random sample of 320 high school students was classified by average nightly sleep
(Less than 7 hours / 7 or more hours) and by GPA category (Below 3.0 / 3.0 or above).

\vspace{8pt}
\renewcommand{\arraystretch}{1.9}
\begin{tabularx}{\linewidth}{@{} l C{3.2cm} C{3.2cm} C{2.4cm} @{}}
\rowcolor{sky}
                          & \textbf{GPA $\geq$ 3.0} & \textbf{GPA $<$ 3.0} & \textbf{Row Total} \\
\hline
\textbf{Sleep $<$ 7 hrs}  & 40 & 80 & \blank{1.8cm} \\
\textbf{Sleep $\geq$ 7 hrs} & 108 & 92 & \blank{1.8cm} \\
\hline
\textbf{Col.\ Total}      & \blank{1.8cm} & \blank{1.8cm} & \blank{1.8cm} \\
\end{tabularx}
\end{tcolorbox}

\vspace{0.18in}

% ── PART 1: CONDITIONAL PROPORTIONS ──────────────────────────────────────────
{\large\bfseries\color{navy} Part 1 \quad Conditional Proportions}

\vspace{0.1in}

\begin{enumerate}

    \item Complete the table by filling in all missing row totals, column totals, and the grand total.

    \vspace{0.08in}

    \item Compute the conditional proportion of students with GPA $\geq$ 3.0 for each sleep group.
          Show your work.\\[10pt]
          $\hat{p}_{\text{low sleep}} = \dfrac{\blank{1.2cm}}{\blank{1.2cm}} = \blank{2.2cm}$
          \hfill
          $\hat{p}_{\text{adequate sleep}} = \dfrac{\blank{1.2cm}}{\blank{1.2cm}} = \blank{2.2cm}$

\end{enumerate}

\vspace{0.22in}

% ── PART 2: DIFFERENCE IN PROPORTIONS ────────────────────────────────────────
{\large\bfseries\color{navy} Part 2 \quad Difference in Proportions}

\vspace{0.1in}

\begin{enumerate}[resume]

    \item Compute the difference in proportions (adequate sleep $-$ low sleep). Show your work.\\[10pt]
          $\hat{p}_{\text{adequate}} - \hat{p}_{\text{low}} = \blank{2cm} - \blank{2cm} = \blank{2.4cm}$

    \vspace{0.16in}

    \item Interpret your answer to \#3 in context using a complete sentence.\\[8pt]
          \writeline\\[2pt]\writeline\\[2pt]\writeline

\end{enumerate}

\vspace{0.22in}

% ── PART 3: RELATIVE RISK ─────────────────────────────────────────────────────
{\large\bfseries\color{navy} Part 3 \quad Relative Risk}

\vspace{0.1in}

\begin{enumerate}[resume]

    \item Compute the relative risk of having a GPA $\geq$ 3.0 for adequate-sleep students
          compared to low-sleep students. Show your work.\\[10pt]
          $\text{RR} = \dfrac{\hat{p}_{\text{adequate}}}{\hat{p}_{\text{low}}}
          = \dfrac{\blank{2cm}}{\blank{2cm}} = \blank{2.4cm}$

    \vspace{0.16in}

    \item Interpret your answer to \#5 in context using a complete sentence.\\[8pt]
          \writeline\\[2pt]\writeline\\[2pt]\writeline

\end{enumerate}

\vspace{0.22in}

% ── PART 4: COMPARISON ────────────────────────────────────────────────────────
{\large\bfseries\color{navy} Part 4 \quad Comparison and Conclusion}

\vspace{0.1in}

\begin{enumerate}[resume]

    \item In 2--3 sentences, write a conclusion about the association between sleep and GPA.
          Include \emph{both} the difference in proportions and relative risk, each in context.\\[8pt]
          \writeline\\[2pt]\writeline\\[2pt]\writeline\\[2pt]\writeline

    \vspace{0.1in}

    \item Which statistic --- the difference in proportions or the relative risk --- do you think
          better communicates the strength of this association? Explain your reasoning.\\[8pt]
          \writeline\\[2pt]\writeline\\[2pt]\writeline

\end{enumerate}

\vspace{0.18in}

% ── AP-STYLE MC ──────────────────────────────────────────────────────────────
\begin{tcolorbox}[colback=redbg, colframe=redacc, boxrule=0.8pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small\textbf{AP-Style Practice}\\[6pt]
Based on your calculations, which of the following best describes the association between
sleep and GPA in this sample?

\vspace{8pt}
\begin{enumerate}[label=\textbf{(\Alph*)}, leftmargin=2em, itemsep=6pt]
  \item There is no association because neither group had a majority with GPA $\geq$ 3.0.
  \item Students with adequate sleep are more likely to have a GPA $\geq$ 3.0, but the
        relative risk is close to 1 so the association is weak.
  \item Students with adequate sleep are more likely to have a GPA $\geq$ 3.0; both the
        difference in proportions and relative risk indicate a meaningful association.
  \item The relative risk cannot be interpreted without knowing the marginal proportions.
\end{enumerate}
\end{tcolorbox}

\vspace{0.1in}
\noindent\textcolor{slate}{\small My answer: \blank{1cm} \quad Because: \blank{8cm}}

\end{document}
