%! AP Statistics — Unit 1, Lesson 1.4 — Exit Ticket
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

%=============================================================================
\begin{document}

\pageheader{Unit 1, Lesson 1.4}{Exit Ticket}
\namedateperiod

\vspace{0.22in}

\begin{tcolorbox}[colback=sky, colframe=navy, boxrule=0.9pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small A survey of \textbf{80 adults} asks: ``What is your favorite TV genre?''
The results are below. Complete the table and then answer the questions.
\end{tcolorbox}

\vspace{0.2in}

\renewcommand{\arraystretch}{2.2}
\begin{tabularx}{\linewidth}{@{} >{\bfseries}p{0.22\linewidth}
                                    C{0.18\linewidth}
                                    C{0.26\linewidth} @{}}
\rowcolor{sky}
\textbf{Genre} & \textbf{Frequency} & \textbf{Rel.\ Frequency} \\
\midrule
News    & 32 & \blank{2.8cm} \\
Sports  & 20 & \blank{2.8cm} \\
Reality & 16 & \blank{2.8cm} \\
Other   & 12 & \blank{2.8cm} \\
\midrule
\rowcolor{sky}\textbf{Total} & \blank{2cm} & \blank{2.8cm} \\
\end{tabularx}

\vspace{0.24in}

\begin{enumerate}[leftmargin=1.5em, itemsep=10pt]

  \item In the box below, sketch a \textbf{relative frequency bar chart} for this
        data. Include: a title, labeled axes, a scale starting at 0, and gaps
        between bars.

\vspace{8pt}
\begin{tcolorbox}[colback=white, colframe=navy, boxrule=0.8pt, arc=2mm,
    left=3mm, right=3mm, top=2mm, bottom=2mm, height=2.2in]
\end{tcolorbox}

  \item Write one complete sentence describing the distribution of TV genre
        preference for these 80 adults in context.\\[6pt]
        \writeline\\[1pt]\writeline

  \item Describe one specific way someone could redraw this bar chart to make
        it misleading. What would a reader incorrectly conclude?\\[6pt]
        \writeline\\[1pt]\writeline

\end{enumerate}

\vspace{0.2in}

% ── AP-STYLE ─────────────────────────────────────────────────────────────────
\begin{tcolorbox}[colback=redbg, colframe=redacc, boxrule=0.8pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small\textbf{AP-Style Practice}\\[6pt]
A bar chart shows the distribution of transportation mode for students at two
schools. School A's bars use frequency; School B's bars use relative frequency.
A student says: ``It's easy to compare the two schools because both schools
have bars for the same categories.''

\vspace{8pt}
Is the student's statement correct? Explain why or why not.\\[8pt]
\writeline\\[1pt]\writeline\\[1pt]\writeline
\end{tcolorbox}

\end{document}
