%! AP Statistics — Unit 3, Lesson 3.4 — Warm-Up
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

\begin{document}

\pageheader{Unit 3, Lesson 3.4}{Warm-Up}
\namedateperiod

\vspace{0.3in}

% ── SECTION 1: Spiral Review ──────────────────────────────────────────────────
{\large\bfseries\color{navy} Part 1 \quad Spiral Review}

\vspace{0.12in}

\begin{enumerate}

    \item From Lesson 3.3 --- match each description to the sampling method.

    \vspace{8pt}
    \renewcommand{\arraystretch}{1.8}
    \begin{tabularx}{\linewidth}{@{} X p{3.2cm} @{}}
    \textbf{Description} & \textbf{Method} \\
    \hline
    Divide the city into zip codes; randomly select 5 zip codes; survey all residents
    in selected zip codes. & \blank{3cm} \\
    Divide employees by department; randomly select 10 from each department. &
    \blank{3cm} \\
    Number all customers 1--2{,}000; select a random start between 1--20; survey every
    20th person after. & \blank{3cm} \\
    \end{tabularx}

    \vspace{0.18in}

    \item Read this survey question: \textit{``Don't you agree that our school's dress
    code is unfair and needs to be changed?''}
    \begin{enumerate}[label=(\alph*), itemsep=4pt]
        \item What is wrong with this question?\\
        \writeline
        \item Rewrite it to be a fair, unbiased question.\\
        \writeline\writeline
    \end{enumerate}

\end{enumerate}

\vspace{0.35in}

% ── SECTION 2: Looking Ahead ──────────────────────────────────────────────────
{\large\bfseries\color{navy} Part 2 \quad Looking Ahead}

\vspace{0.12in}

\noindent Today we study what goes wrong when random sampling fails.

\vspace{0.14in}

\begin{tcolorbox}[colback=greenbg, colframe=greenacc, boxrule=0.8pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
    \small
    \begin{itemize}[leftmargin=1.3em, itemsep=8pt]
  \item \textbf{Voluntary response bias}: only those with strong opinions respond.
  \item \textbf{Undercoverage}: parts of the population are excluded from the sample.
  \item \textbf{Nonresponse}: selected individuals decline to respond; those who
        do may differ from those who don't.
  \item \textbf{Response/question-wording bias}: the question itself or survey context
        distorts answers.
    \end{itemize}
\end{tcolorbox}

\vspace{0.2in}

\noindent\textcolor{slate}{\small Name one situation in real life where you think bias
would be a serious problem:}\\[8pt]
\writeline\\[2pt]\writeline

\end{document}
