%! AP Statistics — Unit 4, Lesson 4.8 — Homework
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}
\newcommand{\TallMath}[1]{$\displaystyle #1\rule[-1.4em]{0pt}{3.2em}$}

\begin{document}

\pageheader{Unit 4, Lesson 4.8}{Homework}
\namedateperiod

\vspace{0.1in}

\begin{practicebox}
\small

\textbf{1.} $X$ = number of customer complaints received per day at a store.
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{@{}cccccc@{}}
$x$ & 0 & 1 & 2 & 3 & 4 \\
\hline
$P(X=x)$ & 0.35 & 0.30 & 0.20 & 0.10 & 0.05 \\
\end{tabular}
\end{center}

\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=6pt]
  \item Compute $\mu_X$ using the computation table below.

\vspace{4pt}
\renewcommand{\arraystretch}{1.9}
\begin{tabularx}{\linewidth}{@{} c c X @{}}
$x$ & $P(X=x)$ & $x \cdot P(X=x)$ \\
\hline
0 & 0.35 & \blank{3cm} \\
1 & 0.30 & \blank{3cm} \\
2 & 0.20 & \blank{3cm} \\
3 & 0.10 & \blank{3cm} \\
4 & 0.05 & \blank{3cm} \\
\hline
& & $\mu_X =$ \blank{2cm} \\
\end{tabularx}

  \item Interpret $\mu_X$ in context.\\
        \writeline\\[1pt]\writeline

  \item Compute $\sigma_X$. (Show your variance computation.)

        \vspace{0.5in}

  \item Interpret $\sigma_X$ in context.\\
        \writeline\\[1pt]\writeline
\end{enumerate}

\vspace{0.14in}

\textbf{2.} A company insures a machine worth \$10{,}000. From historical data, the
probability of a claim in a year is 0.04. If a claim occurs, the company pays \$10{,}000.
Let $X$ = the amount paid.
\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=8pt]
  \item Write the probability distribution for $X$.

        \vspace{0.3in}

  \item Find $\mu_X$. \quad \blank{4cm}
  \item Interpret $\mu_X$ in context.\\
        \writeline\\[1pt]\writeline
\end{enumerate}

\vspace{0.14in}

\textbf{3.} AP-style free response. A random variable $W$ has mean $\mu_W = 4.5$ and
standard deviation $\sigma_W = 2.1$.
\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=8pt]
  \item Interpret $\mu_W = 4.5$ in the context of a random variable representing the
        number of hours a student sleeps on school nights.\\
        \writeline\\[1pt]\writeline

  \item Interpret $\sigma_W = 2.1$ in the same context.\\
        \writeline\\[1pt]\writeline
\end{enumerate}

\end{practicebox}

\vspace{0.1in}

\begin{extensionbox}
\small
\textbf{Extension --- optional.}
A game pays \$0 or \$6, and you want to make it a ``fair game'' (expected net winnings = \$0).
If the game costs \$2 to play, what must $P(\text{win \$6})$ be?
Show your work.\\[4pt]
\writeline\\[1pt]\writeline\\[1pt]\writeline
\end{extensionbox}

\vspace{0.1in}

\begin{blurbbox}[Preview: Lesson 4.9]{sky}
\small
In Lesson 4.9 you will learn the rules for combining random variables: if $X$ and $Y$ are
independent, then $\mu_{X+Y} = \mu_X + \mu_Y$ and $\sigma^2_{X+Y} = \sigma^2_X + \sigma^2_Y$.
Think about why standard deviations don't simply add the way means do.
\end{blurbbox}

\end{document}
