%! AP Statistics — Unit 2, Lesson 2.6 — Exit Ticket
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

\begin{document}

\pageheader{Unit 2, Lesson 2.6}{Exit Ticket}
\namedateperiod

\vspace{0.22in}

% ── SCENARIO ─────────────────────────────────────────────────────────────────
\begin{tcolorbox}[colback=sky, colframe=navy, boxrule=0.9pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small\textit{A statistics teacher recorded the number of hours each student studied for a
unit exam and the score each student earned (out of 100). Using data from 28 students who
studied between 0 and 8 hours, technology produced the following regression equation:}
\[
  \widehat{\text{score}} = 40 + 5(\text{hours})
\]
\end{tcolorbox}

\vspace{0.2in}

\begin{enumerate}[leftmargin=1.6em, itemsep=0.2in]

  \item Interpret the \textbf{slope} ($5$) in context.\\[10pt]
        \writeline\\[3pt]\writeline\\[3pt]\writeline

  \item Interpret the \textbf{$y$-intercept} ($40$) in context.
        State whether it is meaningful in this context.\\[10pt]
        \writeline\\[3pt]\writeline\\[3pt]\writeline

  \item Predict the exam score for a student who studied \textbf{6 hours}.
        Is this interpolation or extrapolation? Show your calculation.\\[10pt]
        \writeline\\[3pt]\writeline\\[3pt]\writeline

  \item A student claims she studied \textbf{30 hours}. Use the equation to compute a
        predicted score. Then explain why this prediction is not trustworthy.\\[10pt]
        \writeline\\[3pt]\writeline\\[3pt]\writeline

\end{enumerate}

\vspace{0.16in}

% ── AP-STYLE MC ──────────────────────────────────────────────────────────────
\begin{tcolorbox}[colback=redbg, colframe=redacc, boxrule=0.8pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small\textbf{AP-Style Practice}\\[6pt]
A researcher fits a regression line for data on $x$ = age of a tree (years) and $y$ = trunk
diameter (cm). The data were collected from trees aged 5 to 30 years. The slope is $1.8$ and
the $y$-intercept is $3.5$. Which of the following is the best interpretation of the slope?

\vspace{10pt}
\begin{enumerate}[label=\textbf{(\Alph*)}, leftmargin=2em, itemsep=6pt]
  \item The predicted trunk diameter of a newly planted tree (age $= 0$) is 3.5 cm.
  \item For every additional centimeter of trunk diameter, the predicted age increases by 1.8 years.
  \item For each additional year of age, the predicted trunk diameter increases by approximately 1.8 cm.
  \item A tree that is 1.8 years old will have a trunk diameter of 3.5 cm.
\end{enumerate}
\end{tcolorbox}

\vspace{0.1in}
\noindent\textcolor{slate}{\small My answer: \blank{1cm} \quad Because: \blank{8cm}}

\end{document}
