%! AP Statistics — Unit 3, Lesson 3.6 — Warm-Up
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

\begin{document}

\pageheader{Unit 3, Lesson 3.6}{Warm-Up}
\namedateperiod

\vspace{0.3in}

% ── SECTION 1: Spiral Review ──────────────────────────────────────────────────
{\large\bfseries\color{navy} Part 1 \quad Spiral Review}

\vspace{0.12in}

\begin{enumerate}

    \item From Lesson 3.5 --- for each experiment, identify the design type (CRD,
    block, or matched pairs).

    \vspace{8pt}
    \renewcommand{\arraystretch}{1.8}
    \begin{tabularx}{\linewidth}{@{} X p{3.2cm} @{}}
    \textbf{Description} & \textbf{Design type} \\
    \hline
    80 patients are randomly assigned to drug or placebo, with no grouping. &
    \blank{3cm} \\
    30 pairs of twins are recruited; one twin in each pair gets the treatment. &
    \blank{3cm} \\
    120 students grouped by GPA quartile; randomly assigned to tutoring conditions
    within each quartile. & \blank{3cm} \\
    \end{tabularx}

    \vspace{0.18in}

    \item Describe the four principles of a well-designed experiment.
    \vspace{6pt}
    \begin{enumerate}[label=(\arabic*), itemsep=8pt]
        \item \blank{11cm}
        \item \blank{11cm}
        \item \blank{11cm}
        \item \blank{11cm}
    \end{enumerate}

\end{enumerate}

\vspace{0.25in}

% ── SECTION 2: Looking Ahead ──────────────────────────────────────────────────
{\large\bfseries\color{navy} Part 2 \quad Looking Ahead}

\vspace{0.12in}

\noindent Today we choose the \emph{best} design for a given research situation.

\vspace{0.14in}

\begin{tcolorbox}[colback=greenbg, colframe=greenacc, boxrule=0.8pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
    \small
    \begin{itemize}[leftmargin=1.3em, itemsep=8pt]
  \item CRD: simplest; best when units are homogeneous.
  \item Block design: use when a nuisance variable is known; increases precision.
  \item Matched pairs: maximum control; works with very small samples.
    \end{itemize}
\end{tcolorbox}

\vspace{0.2in}

\noindent\textcolor{slate}{\small When would you choose a matched-pairs design over a
CRD? Write your reasoning:}\\[8pt]
\writeline\\[2pt]\writeline

\end{document}
