%! AP Statistics — Unit 9, Lesson 9.3 — Homework
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

\begin{document}

\pageheader{Unit 9, Lesson 9.3}{Homework}
\namedateperiod

\vspace{0.1in}
\textbf{Directions:} Show all reasoning clearly. When interpreting a CI, include all
required elements: confidence level, both endpoints with units, and a reference to the
population.

\begin{enumerate}

  \item \textbf{Sleep and GPA.} A random sample of 50 college students was used to study
        the relationship between average hours of sleep per night ($x$) and GPA ($y$).
        Computer output gives a 95\% confidence interval for the slope: $(0.08,\ 0.44)$.

        \begin{enumerate}[label=\alph*.]

          \item Interpret the confidence interval in context.

                \writelines{3}

          \item Does this CI provide evidence that $\beta \ne 0$? Justify.

                \writelines{2}

          \item A professor claims the true slope is $\beta = 0.5$.
                Is this claim consistent with the interval? Explain.

                \writelines{2}

          \item A colleague claims the true slope is $\beta = 0.2$.
                Is this claim consistent with the interval? Explain.

                \writelines{2}

        \end{enumerate}

  \item \textbf{Temperature and Electricity Use.} A researcher collects data from 15 cities
        on average daily temperature ($^\circ$F, $x$) and monthly electricity usage
        (kWh, $y$). A 90\% CI for the slope is $(12.3,\ 31.8)$.

        A second researcher repeats the study with 60 cities and obtains a 90\% CI of
        $(18.1,\ 26.7)$.

        \begin{enumerate}[label=\alph*.]

          \item Interpret the first researcher's CI in context.

                \writelines{3}

          \item Compare the widths of the two CIs. Which is narrower?
                Show your calculations.

                \writelines{3}

          \item Explain why the second CI is narrower, using the concept of standard error.

                \writelines{3}

          \item Do both CIs provide evidence that $\beta \ne 0$? Explain.

                \writelines{2}

        \end{enumerate}

\end{enumerate}

\end{document}
