%! AP Statistics — Unit 8, Lesson 8.3 — Homework
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

\begin{document}

\pageheader{Unit 8, Lesson 8.3}{Homework}
\namedateperiod

\vspace{0.1in}
\textbf{Directions:} Show all work for full credit. Write complete sentences for
interpretations and conclusions.

\begin{enumerate}

  \item \textbf{Genetics.} According to Mendelian genetics, offspring from a specific
        cross are expected to appear in a 9:3:3:1 ratio across 4 phenotype categories.
        A researcher observes the following counts in a random sample of 160 offspring:

        \renewcommand{\arraystretch}{1.4}
        \begin{center}
        \begin{tabular}{lcccc}
            \textbf{Phenotype} & 1  & 2  & 3  & 4  \\
            \hline
            \textbf{Observed}  & 89 & 31 & 27 & 13 \\
        \end{tabular}
        \end{center}

        \begin{enumerate}[label=\alph*.]
          \item Calculate the expected count for each phenotype under the 9:3:3:1 ratio.
                \writelines{2}
          \item Calculate the chi-square test statistic. Show all four
                $(O - E)^2 / E$ contributions.
                \writelines{4}
          \item State the degrees of freedom: $df =$ \blank{2cm}
          \item The p-value is approximately 0.81. State a complete conclusion at
                $\alpha = 0.05$.
                \writelines{2}
        \end{enumerate}

  \item \textbf{Streaming Services.} A survey of 200 college students asks which of
        5 streaming services they use most. If students chose equally among the options,
        each service would account for 20\% of responses. The observed counts are:

        \renewcommand{\arraystretch}{1.4}
        \begin{center}
        \begin{tabular}{lccccc}
            \textbf{Service}  & Netflix & Hulu & Disney+ & Amazon & Other \\
            \hline
            \textbf{Observed} & 78      & 42   & 35      & 28     & 17    \\
        \end{tabular}
        \end{center}

        \begin{enumerate}[label=\alph*.]
          \item State $H_0$ and $H_a$ for a chi-square goodness-of-fit test.
                \writelines{2}
          \item Calculate the expected count for each service and compute the
                chi-square test statistic. Show your work.
                \writelines{5}
          \item State the degrees of freedom: $df =$ \blank{2cm}
          \item The p-value is less than 0.001. Interpret this p-value in context,
                then state a complete conclusion at $\alpha = 0.05$.
                \writelines{3}
        \end{enumerate}

  \item \textbf{Conceptual Question.} After completing a chi-square goodness-of-fit test,
        a student writes: \textit{``Because we fail to reject $H_0$, we have proved that
        the distribution of the population matches the null proportions.''}

        Explain the error in this statement.

        \writelines{3}

\end{enumerate}

\end{document}
