%! AP Statistics — Unit 1, Lesson 1.3 — Exit Ticket
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

%=============================================================================
\begin{document}

\pageheader{Unit 1, Lesson 1.3}{Exit Ticket}
\namedateperiod

\vspace{0.22in}

\begin{tcolorbox}[colback=sky, colframe=navy, boxrule=0.9pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small A survey of \textbf{50 students} asks: ``Where do you prefer to study?''
The frequency table below is partially complete. Fill in the missing values
and then answer the questions.
\end{tcolorbox}

\vspace{0.2in}

\renewcommand{\arraystretch}{2.2}
\begin{tabularx}{\linewidth}{@{} >{\bfseries}p{0.24\linewidth}
                                    C{0.2\linewidth}
                                    C{0.26\linewidth} @{}}
\rowcolor{sky}
\textbf{Location} & \textbf{Frequency} & \textbf{Rel.\ Frequency} \\
\midrule
Library  & 18 & \blank{2.8cm} \\
Home     & 22 & \blank{2.8cm} \\
Caf\'{e} & 6  & \blank{2.8cm} \\
Other    & 4  & \blank{2.8cm} \\
\midrule
\rowcolor{sky}\textbf{Total} & \blank{2cm} & \blank{2.8cm} \\
\end{tabularx}

\vspace{0.24in}

\begin{enumerate}[leftmargin=1.5em, itemsep=10pt]

  \item Write one complete sentence describing the most common study location
        \textit{in context}.\\[6pt]
        \writeline\\[1pt]\writeline

  \item What percentage of students study somewhere other than home?
        Show your work.\\[8pt]
        \writeline\\[1pt]\writeline

\end{enumerate}

\vspace{0.2in}

% ── AP-STYLE ─────────────────────────────────────────────────────────────────
\begin{tcolorbox}[colback=redbg, colframe=redacc, boxrule=0.8pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm]
\small\textbf{AP-Style Practice}\\[6pt]
A table shows the distribution of eye color for a sample of 200 people.
The relative frequencies are: Brown~0.42, Blue~0.28, Hazel~0.18, Other~0.12.

\vspace{10pt}
\begin{enumerate}[label=\textbf{(\Alph*)}, leftmargin=2em, itemsep=6pt]
  \item What proportion of people in the sample have brown or hazel eyes?
        Show your calculation.
  \item Write one or two sentences describing the distribution of eye color
        in this sample.
\end{enumerate}

\vspace{10pt}
\textbf{(A)} Answer: \blank{6cm}\\[10pt]
\textbf{(B)} \writeline\\[1pt]\writeline

\end{tcolorbox}

\end{document}
