%! AP Statistics — Unit 4, Lesson 4.1 — Group Activity
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

\begin{document}

\pageheader{Unit 4, Lesson 4.1}{Group Activity: Real or Random?}
\namepartnerperiod

\vspace{0.1in}

\begin{scenariobox}[Context]{sky}
\small
For each scenario below, your group will (1) identify the pattern observed, (2) write a
statistical question it suggests, (3) decide whether chance alone is a plausible
explanation, and (4) describe what additional evidence would confirm a non-random cause.
Work through all tiers your teacher assigns.
\end{scenariobox}

\vspace{0.1in}

% ── Tier R ────────────────────────────────────────────────────────────────────
\begin{tcolorbox}[colback=goldbg, colframe=goldacc, boxrule=1pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm,
    title={\bfseries Tier R \enspace Remediate --- Getting Started with Patterns}]
\small

\textbf{Scenario 1:} A student rolls a standard die 20 times and records:
\[
1,\ 3,\ 5,\ 5,\ 5,\ 2,\ 4,\ 6,\ 5,\ 1,\ 3,\ 2,\ 5,\ 5,\ 4,\ 6,\ 1,\ 2,\ 3,\ 5
\]

\begin{enumerate}[leftmargin=1.5em, itemsep=8pt]
  \item How many times did 5 appear? \blank{3cm}
  \item Is that more or less than you would expect from a fair die?\\
        \writeline
  \item Circle one: \quad This pattern \textbf{proves} the die is unfair. \quad /
        \quad This pattern \textbf{suggests a question} about the die.
  \item Write that question here: \writeline\writeline
\end{enumerate}

\vspace{8pt}
\textbf{Scenario 2:} Your school basketball team wins 8 games in a row after losing
their first 3 games of the season.

\begin{enumerate}[leftmargin=1.5em, itemsep=8pt]
  \item Describe the pattern in one sentence: \writeline
  \item Does winning 8 in a row \emph{prove} the team ``found their game''? Circle: Yes / No
  \item Write a question this streak suggests: \writeline\writeline
\end{enumerate}

\end{tcolorbox}

\vspace{0.1in}

% ── Tier A ────────────────────────────────────────────────────────────────────
\begin{tcolorbox}[colback=greenbg, colframe=greenacc, boxrule=1pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm,
    title={\bfseries Tier A \enspace Approaching Proficiency --- Patterns and Statistical Questions}]
\small

\textbf{Scenario 3:} A county health department reports that 11 people in a
neighborhood of 400 were diagnosed with a rare liver condition last year. Nationally,
the rate is about 1 in 200 (0.5\%).

\begin{enumerate}[leftmargin=1.5em, itemsep=8pt]
  \item What is the observed rate in this neighborhood? Show your calculation.
        \vspace{14pt}
  \item How does it compare to the national rate? \writeline
  \item Write a statistical question this pattern suggests: \writeline\writeline
  \item Could this cluster arise by chance? Explain your reasoning.\\
        \writeline\writeline
  \item What evidence would make you more confident it is NOT random?\\
        \writeline\writeline
\end{enumerate}

\vspace{8pt}
\textbf{Scenario 4:} On a social media platform, a celebrity's post receives ``likes''
at a rate of about 12{,}000 per hour for the first 6 hours, then suddenly jumps to
80{,}000 per hour for the next 2 hours.

\begin{enumerate}[leftmargin=1.5em, itemsep=8pt]
  \item Describe the pattern: \writeline
  \item Write a statistical question: \writeline\writeline
  \item Is chance a plausible explanation for the jump? Why or why not?\\
        \writeline\writeline
\end{enumerate}

\end{tcolorbox}

\vspace{0.1in}

% ── Tier E ────────────────────────────────────────────────────────────────────
\begin{tcolorbox}[colback=sky, colframe=navy, boxrule=1pt, arc=2mm,
    left=4mm, right=4mm, top=3mm, bottom=3mm,
    title={\bfseries Tier E \enspace Extension --- Deeper Analysis}]
\small

\textbf{Scenario 5:} Researchers tracked the daily high temperature in a city for
30 consecutive days. The data showed 9 days above 90°F in a row (days 14--22), while
the historical average for that month is 3 days above 90°F per 30-day period.

\begin{enumerate}[leftmargin=1.5em, itemsep=8pt]
  \item How many consecutive 90°F+ days were observed? \blank{3cm}
  \item Write a precise statistical question this pattern suggests.\\
        \writeline\writeline
  \item A skeptic says: ``Temperatures are not independent from day to day --- a hot
        day makes the next day more likely to be hot too.'' How does this complicate
        the question of whether the streak is random?\\
        \writeline\writeline\writeline
  \item Describe a study design that could help determine whether climate change (a
        non-random cause) is responsible for the streak.\\
        \writeline\writeline\writeline
\end{enumerate}

\end{tcolorbox}

\end{document}
