%! AP Statistics — Unit 3, Lesson 3.4 — Homework
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

\begin{document}

\pageheader{Unit 3, Lesson 3.4}{Homework}
\namedateperiod

\vspace{0.1in}

\begin{practicebox}
\small
For each survey, (a) identify the type of bias, (b) explain how it distorts the
estimate (direction), and (c) suggest an improvement.

\vspace{8pt}
\textbf{1.} A radio station asks listeners to call in and answer: ``Do you think
schools should start later?'' 78\% of 2{,}400 callers say yes.

\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=7pt]
  \item Type of bias: \blank{8cm}
  \item Direction and explanation: \writeline\\[1pt]\writeline
  \item Improvement: \writeline
\end{enumerate}

\vspace{8pt}
\textbf{2.} A phone survey randomly selects households from a list of landline
numbers to ask about online shopping habits.

\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=7pt]
  \item Type of bias: \blank{8cm}
  \item Who is excluded? \writeline
  \item How does this distort the estimate of online shopping frequency?
        \writeline\\[1pt]\writeline
\end{enumerate}

\vspace{8pt}
\textbf{3.} Researchers ask college students: ``Don't you think the university
should invest more in mental health resources?''

\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=7pt]
  \item Type of bias: \blank{8cm}
  \item Rewrite the question to remove the bias: \writeline
  \item Direction: the estimate of support will be too \blank{3cm} because
        \blank{7cm}
\end{enumerate}

\vspace{8pt}
\textbf{4.} A researcher randomly selects 800 adults but only 200 complete the survey.

\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=7pt]
  \item Was the initial selection biased? \blank{3cm}
  \item What bias affects the completed surveys? \blank{6cm}
  \item How could this distort the results? \writeline\\[1pt]\writeline
\end{enumerate}
\end{practicebox}

\end{document}
