%! AP Statistics — Unit 9, Lesson 9.4 — Group Activity
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

\begin{document}

\pageheader{Unit 9, Lesson 9.4}{Group Activity}
\namepartnerperiod

\vspace{0.1in}
\textbf{Setting Up a Significance Test for Slope}

\vspace{0.05in}
\textbf{Scenario 1:} A nutritionist randomly selects 40 adults and records their
daily fiber intake (grams, $x$) and LDL cholesterol (mg/dL, $y$). A residual plot
shows random scatter around zero with roughly equal spread. A histogram of residuals
is approximately bell-shaped. She wants to test whether fiber intake is linearly
related to LDL cholesterol.

\vspace{0.05in}
\textbf{Scenario 2:} A realtor randomly selects 50 homes sold in a city and records
square footage ($x$) and sale price (\$1000s, $y$). The residual plot shows random
scatter with no curve and roughly equal spread. $n = 50$ so normality is reasonable.
She wants to test whether square footage linearly predicts sale price.

\vspace{0.1in}
\textbf{Directions:} Complete the setup at your tier.

\begin{tcolorbox}[colback=white, colframe=black!40,
    title=\textbf{Tier R --- Remediate},
    fonttitle=\bfseries, arc=2mm, left=3mm, right=3mm, top=2mm, bottom=2mm]

\textbf{Use Scenario 1 only.}

\begin{enumerate}[label=\alph*.]

  \item Name the appropriate test: \blank{7cm}

  \item Define $\beta$: ``the true slope of the regression line relating
        \blank{4cm} to \blank{4cm} for \blank{4cm}.''

  \item H$_0$: $\beta = $ \blank{1.5cm} \qquad H$_a$: $\beta$ \blank{1.5cm} 0
        \quad (circle one: \quad $<$ \quad $\ne$ \quad $>$)

  \item For each LINER condition, circle YES (met), NO (violated), or N/A
        (cannot verify from the given information):

        \begin{tabularx}{\linewidth}{lXccc}
            \textbf{Letter} & \textbf{Condition} & \textbf{Met?} \\
            \hline
            L & Random scatter in residual plot & YES \quad / \quad NO \quad / \quad N/A \\
            I & Random sample; 10\% condition   & YES \quad / \quad NO \quad / \quad N/A \\
            N & Residuals bell-shaped            & YES \quad / \quad NO \quad / \quad N/A \\
            E & Equal spread in residual plot    & YES \quad / \quad NO \quad / \quad N/A \\
        \end{tabularx}

\end{enumerate}
\end{tcolorbox}

\begin{tcolorbox}[colback=white, colframe=black!40,
    title=\textbf{Tier A --- Approaching Proficiency},
    fonttitle=\bfseries, arc=2mm, left=3mm, right=3mm, top=2mm, bottom=2mm]

Complete \textbf{both} Scenario 1 and Scenario 2. For each:

\begin{enumerate}[label=\alph*.]

  \item Name the appropriate test.

        Scenario 1: \blank{6cm} \qquad Scenario 2: \blank{6cm}

  \item Define $\beta$ in context and state H$_0$ and H$_a$ for each scenario.

        \textit{Scenario 1:} $\beta = $ \writeline
        H$_0$: \blank{8cm} \quad H$_a$: \blank{8cm}

        \vspace{0.05in}
        \textit{Scenario 2:} $\beta = $ \writeline
        H$_0$: \blank{8cm} \quad H$_a$: \blank{8cm}

  \item Verify each LINER condition for both scenarios using the information given.
        State whether each is met and explain briefly.

        \writelines{4}

  \item Is there any condition you cannot fully verify from the given information?
        Which one, and why?

        \writelines{2}

\end{enumerate}
\end{tcolorbox}

\begin{tcolorbox}[colback=white, colframe=black!40,
    title=\textbf{Tier E --- Extension},
    fonttitle=\bfseries, arc=2mm, left=3mm, right=3mm, top=2mm, bottom=2mm]

Complete all of Tier A above. Then answer the following:

\begin{enumerate}[label=\alph*., start=5]

  \item For Scenario 2, the realtor suspects the relationship is positive (larger
        homes cost more). Should she use a one-sided or two-sided alternative?
        Write the specific H$_a$ she would use.

        \writelines{2}

  \item Why is it almost always better to use a two-sided alternative unless you
        have a strong prior reason to use one-sided?

        \writelines{2}

\end{enumerate}
\end{tcolorbox}

\end{document}
