%! AP Statistics — Unit 3, Lesson 3.4 — Student Guided Notes
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

\begin{document}

\pageheader{Unit 3, Lesson 3.4}{Guided Notes}
\namedateperiod

\vspace{0.12in}

\begin{objectivebox}
\small By the end of this lesson, I will be able to\dots\\[4pt]
\writeline\\[1pt]
\writeline\\[1pt]
\writeline
\end{objectivebox}

\vspace{0.1in}

\begin{vocabbox}
\termblanklong{Bias}
\termblanklong{Voluntary response bias}
\termblanklong{Undercoverage bias}
\termblanklong{Nonresponse bias}
\termblanklong{Response bias}
\end{vocabbox}

\vspace{0.1in}

\begin{notesbox}{Types of Bias in Sampling}
\small
\textbf{Bias} occurs when certain responses are systematically \blank{5cm} over others
(DAT-2.E.1).

\vspace{8pt}
\renewcommand{\arraystretch}{2.2}
\begin{tabularx}{\linewidth}{@{} >{\bfseries\color{navy}}p{0.26\linewidth}
    >{\raggedright\arraybackslash}p{0.38\linewidth}
    >{\raggedright\arraybackslash}X @{}}
\textbf{Bias type} & \textbf{What causes it} & \textbf{Example} \\
\hline
Voluntary response & Only \blank{4cm} respond --- usually those with strong opinions. &
\blank{5cm} \\
Undercoverage & Part of the population has a \blank{3cm} chance of being included. &
\blank{5cm} \\
Nonresponse & Selected individuals who \blank{3cm} to respond differ from those who do. &
\blank{5cm} \\
Response / question-wording & The \blank{3cm} instrument or \blank{3cm} context
distorts answers. &
\blank{5cm} \\
\end{tabularx}
\end{notesbox}

\vspace{0.1in}

\begin{notesbox}{Diagnosing Bias on the AP Exam}
\small
A complete answer on the AP exam must:
\begin{enumerate}[itemsep=4pt]
  \item \textbf{Name} the type of bias: \blank{7cm}
  \item \textbf{Explain the mechanism}: who is over- or under-represented and why:
        \blank{7cm}
  \item \textbf{State the direction}: the estimate is too \blank{2cm} because
        \blank{5cm}
\end{enumerate}

\vspace{8pt}
\textbf{Key fact:} A \blank{2cm} non-random sample does \textbf{not} fix bias.
More responses of a biased type just give more of the same \blank{3cm}.
\end{notesbox}

\vspace{0.1in}

\begin{practicebox}
\small For each survey, identify the bias type and state the direction of distortion.
\begin{enumerate}[leftmargin=1.5em, itemsep=10pt]
  \item A news channel asks viewers to text ``YES'' or ``NO'' on a political issue.\\
        Bias type: \blank{5cm} \quad Direction: \blank{6cm}

  \item A political poll only calls landlines (no cell phones). Young adults are
        primarily cell-phone-only.\\
        Bias type: \blank{5cm} \quad Direction: \blank{6cm}

  \item A survey asks: ``Would you support cutting wasteful government spending?''\\
        Bias type: \blank{5cm} \quad Direction: \blank{6cm}
\end{enumerate}
\end{practicebox}

\end{document}
