%! AP Statistics — Unit 9, Lesson 9.1 — Homework
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

\begin{document}

\pageheader{Unit 9, Lesson 9.1}{Homework}
\namedateperiod

\vspace{0.1in}

\textbf{Problem 1.} A student fits a least-squares regression line to data on daily
temperature ($^\circ$F, $x$) and the number of hot drinks sold at a caf\'e ($y$) from a
random sample of 20 days. The equation is $\hat{y} = 85 - 1.4x$.

\begin{enumerate}[label=\alph*.]

  \item Interpret the slope in context.

        \writelines{2}

  \item The student concludes: ``Temperature causes fewer hot drinks to be sold because
        the slope is negative.'' Identify \textbf{two} problems with this conclusion.

        Problem 1: \writelines{2}

        Problem 2: \writelines{2}

  \item A second study using $n = 200$ days finds $b = -1.4$ as well. In which study
        would the slope be more convincing evidence of a real relationship? Explain.

        \writelines{3}

\end{enumerate}

\vspace{0.15in}

\textbf{Problem 2.} For each scatter plot description below, state the question a
statistician would ask about the population. Write your answer as a hypothesis
statement (e.g., ``$H_0\colon \beta = 0$ means \ldots'').

\begin{enumerate}[label=\alph*.]

  \item A scatter plot of shoe size ($x$) vs.\ height (inches, $y$) for 50 adults shows
        a positive trend with $b = 0.62$.

        \writelines{3}

  \item A scatter plot of study hours ($x$) vs.\ exam score ($y$) for 8 students shows
        $b = 4.5$, but the points are very scattered around the line.

        \writelines{3}

  \item A scatter plot of screen time (hours, $x$) vs.\ sleep duration (hours, $y$) for
        100 teens shows $b = -0.15$ with little scatter around the line.

        \writelines{3}

\end{enumerate}

\end{document}
