%! AP Statistics — Unit 4, Lesson 4.6 — Homework
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

\begin{document}

\pageheader{Unit 4, Lesson 4.6}{Homework}
\namedateperiod

\vspace{0.1in}

\begin{practicebox}
\small
A streaming service surveyed 300 subscribers about their age group and their
most-used content type. The results are shown below.

\vspace{6pt}
\renewcommand{\arraystretch}{1.4}
\begin{tabularx}{\linewidth}{@{} l X X X r @{}}
 & \textbf{Movies} & \textbf{TV Series} & \textbf{Documentaries} & \textbf{Total} \\
\hline
\textbf{Under 25}  & 50 & 60 & 10 & 120 \\
\textbf{25--44}    & 40 & 50 & 30 & 120 \\
\textbf{45+}       & 20 & 20 & 20 & 60  \\
\hline
\textbf{Total}     & 110 & 130 & 60 & 300 \\
\end{tabularx}

\vspace{8pt}
One subscriber is selected at random.

\vspace{8pt}
\textbf{1.} Test whether ``Movies'' and ``Under 25'' are independent. Show the
independence check with both probabilities, and write a complete conclusion.
\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=6pt]
  \item $P(\text{Movies}) = $ \blank{5cm}
  \item $P(\text{Movies} | \text{Under 25}) = $ \blank{5cm}
  \item Are the events independent? Write a complete sentence explanation.\\
        \writeline\writeline
\end{enumerate}

\vspace{8pt}
\textbf{2.} Use the addition rule to compute $P(\text{TV Series or 25--44})$.
Show all work.\\
\writeline\\[1pt]\writeline

\vspace{8pt}
\textbf{3.} Use the addition rule to compute $P(\text{Movies or Documentaries})$.
\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=6pt]
  \item Are Movies and Documentaries mutually exclusive? \blank{3cm} Why? \writeline
  \item Apply the addition rule (using the correct value of $P(A \cap B)$).\\
        \writeline\writeline
\end{enumerate}

\vspace{8pt}
\textbf{4.} A student claims: ``TV Series and Under 25 are independent because
being Under 25 doesn't \emph{cause} you to watch TV Series.''
\begin{enumerate}[label=(\alph*), leftmargin=2em, itemsep=6pt]
  \item Is this reasoning about independence correct? What is the actual test?\\
        \writeline\writeline
  \item Use the table to determine whether these events actually are independent.\\
        \writeline\writeline
\end{enumerate}

\vspace{8pt}
\textbf{5.} (AP Free-Response Style) Determine whether ``45+'' age group and
``Documentaries'' are independent. Show all calculations and write a complete
interpretation in context.\\
\writeline\\[1pt]\writeline\\[1pt]\writeline\\[1pt]\writeline

\vspace{8pt}
\textbf{6.} (Extension) Prove or disprove: If $P(A) = P(A|B)$, then
$P(B) = P(B|A)$. Use the conditional probability formula in your argument.\\
\writeline\\[1pt]\writeline\\[1pt]\writeline
\end{practicebox}

\end{document}
