%! AP Statistics — Unit 1, Lesson 1.1 — Student Guided Notes
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-boxes}

%=============================================================================
\begin{document}

\pageheader{Unit 1, Lesson 1.1}{Guided Notes}
\namedateperiod

\vspace{0.12in}

% ── OBJECTIVE ────────────────────────────────────────────────────────────────
\begin{objectivebox}
\small By the end of this lesson, I will be able to\dots\\[4pt]
\writeline\\[1pt]
\writeline\\[1pt]
\writeline
\end{objectivebox}

\vspace{0.1in}

% ── VOCABULARY ───────────────────────────────────────────────────────────────
\begin{vocabbox}
\termblanklong{Statistics}
\termblanklong{Individual}
\termblanklong{Population}
\termblanklong{Sample}
\termblanklong{Census}
\termblanklong{Variability / Variation}
\termblanklong{Data}
\termblanklong{Anecdotal evidence}
\end{vocabbox}

\vspace{0.1in}

% ── HOOK ─────────────────────────────────────────────────────────────────────
\begin{hookbox}
\small\textbf{Headline:}\quad
\textit{``Students who sleep more score higher on tests.''}
\hfill\textcolor{slate}{\small(national education study, $n = 12{,}000$)}

\vspace{6pt}
\textbf{Discussion questions — write your thoughts:}
\begin{enumerate}[leftmargin=1.5em, itemsep=2pt]
  \item How do researchers know this? Did they study every student in the world?\\
        \writeline\\[1pt]\writeline

  \item Could this finding be wrong? What would make you doubt it?\\
        \writeline\\[1pt]\writeline

  \item What information would you want before trusting this headline?\\
        \writeline\\[1pt]\writeline
\end{enumerate}
\end{hookbox}

\vspace{0.1in}

% ── DIRECT INSTRUCTION: 4-STEP PROCESS ───────────────────────────────────────
\begin{notesbox}{The Statistical Problem-Solving Process}
\small Fill in each step and what it involves.
\vspace{4pt}

\renewcommand{\arraystretch}{1.5}
\begin{tabularx}{\linewidth}{@{} >{\centering\arraybackslash\columncolor{navy}}p{0.18\linewidth} @{\quad$\longrightarrow$\quad} X @{}}
\textcolor{white}{\textbf{Step 1}} &
  \textbf{Ask a \blank{2.5cm}} \quad
  \textcolor{slate}{\scriptsize Pose a clear question about a \blank{2.5cm} of interest.}\\

\textcolor{white}{\textbf{Step 2}} &
  \textbf{Collect \blank{2.5cm}} \quad
  \textcolor{slate}{\scriptsize Select a \blank{1.8cm} and measure \blank{1.8cm} on each individual.}\\

\textcolor{white}{\textbf{Step 3}} &
  \textbf{Analyze the \blank{2.2cm}} \quad
  \textcolor{slate}{\scriptsize \blank{2.5cm} and \blank{2.5cm} what you found.}\\

\textcolor{white}{\textbf{Step 4}} &
  \textbf{Interpret \blank{2.5cm}} \quad
  \textcolor{slate}{\scriptsize Draw \blank{2cm}; acknowledge what the data \blank{2cm}.}\\
\end{tabularx}
\end{notesbox}

\vspace{0.1in}

% ── CONCEPT NOTES ─────────────────────────────────────────────────────────────
\begin{notesbox}{Key Concepts}
\small
\begin{multicols}{2}

\textbf{\textcolor{navy}{Population vs. Sample}}\\
\textit{Example:} A researcher surveys 200 adults about exercise habits.
\begin{itemize}[itemsep=2pt]
  \item Individual: \blank{3.5cm}
  \item Population: \blank{3.5cm}
  \item Sample: \blank{3.5cm}
  \item Variable: \blank{3.5cm}
\end{itemize}

\vspace{4pt}
\textbf{Why use a sample instead of a census?}\\
\writeline\\[1pt]\writeline

\columnbreak

\textbf{\textcolor{navy}{Why Statistics Needs Variation}}\\[3pt]
Complete the statement:\\[4pt]
\textit{``If every individual were identical, we would \blank{2cm}
need statistics, because there would be \blank{2cm}
\blank{2cm} to explain or measure.''}

\vspace{6pt}
\textbf{What does ``variation'' look like in data?}\\
\textit{Example from class — sleep minutes:}\\[4pt]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
\rule{0pt}{10pt} & & & & \\
\hline
\end{tabular}
\end{center}
\vspace{2pt}
\textit{Min:\;\blank{1cm}\quad Max:\;\blank{1cm}\quad ``Typical'':\;\blank{1.5cm}}

\end{multicols}
\end{notesbox}

\vspace{0.1in}

% ── GUIDED PRACTICE ──────────────────────────────────────────────────────────
\begin{practicebox}
\small\textbf{Scenario Analysis} \hfill \textcolor{slate}{\scriptsize Use your group's assigned scenario}

\vspace{5pt}
\textit{Scenario:} \writeline

\vspace{4pt}
\begin{tabularx}{\linewidth}{@{} l X @{}}
\textbf{Individual:}   & \blank{8cm} \\[6pt]
\textbf{Population:}   & \blank{8cm} \\[6pt]
\textbf{Sample:}       & \blank{8cm} \\[6pt]
\textbf{Variable(s):}  & \blank{8cm} \\[6pt]
\end{tabularx}

\vspace{4pt}
\textbf{Is a census feasible? Why or why not?}\\
\writeline\\[1pt]\writeline

\vspace{4pt}
\textbf{Record one key insight from another group's scenario:}\\
\writeline\\[1pt]\writeline
\end{practicebox}

\vspace{0.1in}

% ── SPIRAL / BIG IDEAS ────────────────────────────────────────────────────────
\begin{spiralbox}
\small
\begin{multicols}{2}

\textbf{This lesson connects forward to\dots}
\begin{itemize}[itemsep=2pt]
  \item \textbf{Lesson 1.2:} Types of variables (categorical vs.\ quantitative)
  \item \textbf{Units 6--9:} Using samples to make \emph{inferences} about populations
  \item \textbf{Unit 3:} How we \emph{collect} samples matters for conclusions
\end{itemize}

\columnbreak

\textbf{Big Idea — Write it in your own words:}\\
\textit{What is the point of statistics?}\\[2pt]
\writeline\\[1pt]\writeline\\[1pt]\writeline

\end{multicols}
\end{spiralbox}

\vspace{0.1in}

% ── EXTRA NOTES ──────────────────────────────────────────────────────────────
\begin{notesbox}{Additional Notes}
\vspace{0pt}
\writeline\\\writeline\\\writeline\\\writeline\\\writeline\\\writeline
\end{notesbox}

\end{document}
