%! AP Statistics — Unit 8, Lesson 8.2 — Group Activity (Answer Key)
\documentclass[10pt]{article}
\usepackage{apstats-article}
\usepackage{apstats-key}

\begin{document}

\pageheader{Unit 8, Lesson 8.2}{Group Activity --- Answer Key}
\namepartnerperiod

\vspace{0.1in}
\textbf{M\&M Color Distribution Study}

The Mars company claims the following color proportions for plain M\&Ms:
Red 13\%, Orange 20\%, Yellow 14\%, Green 16\%, Blue 24\%, Brown 13\%.
Random sample: $n = 200$ M\&Ms.

\begin{tcolorbox}[colback=white, colframe=black!40,
    title=\textbf{Tier R --- Remediate},
    fonttitle=\bfseries, arc=2mm, left=3mm, right=3mm, top=2mm, bottom=2mm]

H$_0$: \ans{are equal to the claimed values: $p_\text{red} = 0.13$, $p_\text{orange} = 0.20$,
$p_\text{yellow} = 0.14$, $p_\text{green} = 0.16$, $p_\text{blue} = 0.24$, $p_\text{brown} = 0.13$.}

H$_a$: \ans{one color proportion differs from the claimed value.}

\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lccc}
    \textbf{Color} & \textbf{Null proportion ($p_0$)} & \textbf{Expected count ($E = 200 \cdot p_0$)} \\
    \hline
    Red    & 0.13 & \ans{26} \\
    Orange & 0.20 & \ans{40} \\
    Yellow & 0.14 & \ans{28} \\
    Green  & 0.16 & \ans{32} \\
    Blue   & 0.24 & \ans{48} \\
    Brown  & 0.13 & \ans{26} \\
\end{tabular}
\end{center}

All expected counts $\ge 5$? \ans{Yes --- smallest is 26. Large Counts condition is met.}

\end{tcolorbox}

\begin{tcolorbox}[colback=white, colframe=black!40,
    title=\textbf{Tier A --- Approaching Proficiency},
    fonttitle=\bfseries, arc=2mm, left=3mm, right=3mm, top=2mm, bottom=2mm]

\begin{enumerate}[label=\alph*.]

  \item H$_0$: \ansline{$p_\text{red} = 0.13$, $p_\text{orange} = 0.20$,
        $p_\text{yellow} = 0.14$, $p_\text{green} = 0.16$,
        $p_\text{blue} = 0.24$, $p_\text{brown} = 0.13$.}

        H$_a$: \ansline{At least one of these color proportions is not as stated.}

  \item \begin{center}
        \renewcommand{\arraystretch}{1.4}
        \begin{tabular}{lccc}
            \textbf{Color} & \textbf{Null proportion ($p_0$)} & \textbf{Expected count ($E$)} \\
            \hline
            Red    & 0.13 & \ans{26} \\
            Orange & 0.20 & \ans{40} \\
            Yellow & 0.14 & \ans{28} \\
            Green  & 0.16 & \ans{32} \\
            Blue   & 0.24 & \ans{48} \\
            Brown  & 0.13 & \ans{26} \\
            \hline
            \textbf{Total} & 1.00 & \ans{200} \\
        \end{tabular}
        \end{center}

  \item \ansline{All expected counts are $\ge 5$ (smallest is 26). Large Counts condition is met.}

  \item \ansline{We would need to know the total number of M\&Ms produced (population size $N$),
        and verify that $n = 200 \le 10\% \cdot N$, i.e., that the bag was selected randomly and
        that 200 is at most 10\% of the production lot.}

\end{enumerate}
\end{tcolorbox}

\begin{tcolorbox}[colback=white, colframe=black!40,
    title=\textbf{Tier E --- Extension},
    fonttitle=\bfseries, arc=2mm, left=3mm, right=3mm, top=2mm, bottom=2mm]

\begin{teachernote}
    Accept any reasonable categorical variable (e.g., blood types, die faces, survey responses).
    Key checks: proportions must sum to 1; minimum sample size is determined by finding
    $n$ such that $n \cdot p_\text{min} \ge 5$, so $n \ge 5 / p_\text{min}$.
    Students should explicitly cite the one-categorical-variable requirement for GOF.
\end{teachernote}
\end{tcolorbox}

\end{document}
